---
title: "Reasonableness_Medians_072025"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 5
    df_print: paged
---

This is the formal analysis file for the "The Nature of Reasonableness" by by Kevin Tobia, Ivar R. Hannikainen, David Kamper, Guilherme Almeida, Piotr Bystranowski, Niek Strohmaier, Vilius Dranseika, Markus Kneer, Fernando Aguiar, Kristina Dolinina, Bartosz Janik, Eglė Lauraitytė, Alice Liefgreen, Maciej Próchnicki, Alejandro Rosas, Vivek Kumar Shukla, and Noel Struchiner (2025, Stanford Journal of International Law).

## Introduction and Loading of Files

```{r}
# Load Libraries

library(dplyr)
library(tidyverse)
library(stats)
library(ggplot2)
library(ggthemes)
library(corrplot)
library(gridExtra)
library(kableExtra)
library(effects)
library(scales)
```

```{r}
DATA_PATH <- "/Users/dgkamper/Library/CloudStorage/GoogleDrive-dgkamper@gmail.com/My Drive/DGK Lab/Collaborations/Language and Law Laboratory/Analysis/LegalResonablenessAnalysis/Data_all_numeric.csv"
```

#### 1. Initial Data Loading and Preparation

```{r}
# Read the data from specified path
Data_All <- read.csv(DATA_PATH, stringsAsFactors = FALSE)

# Verify data structure
glimpse(Data_All)
```

#### 2. Exclude participants whose answer to Q19 does not equal 15 [comprehension/attention question].

```{r}
# Split data by condition
Data_All_Average <- Data_All %>% filter(Condition_name == "Average")
Data_All_Ideal <- Data_All %>% filter(Condition_name == "Ideal")
Data_All_Reasonable <- Data_All %>% filter(Condition_name == "Reasonable")

# Exclude participants whose answer to Q19 does not equal 15 [comprehension/attention question].
Data_All_Average_Pass1 <- Data_All_Average %>% filter(q19 == 15)
Data_All_Ideal_Pass1 <- Data_All_Ideal %>% filter(q19 == 15)
Data_All_Reasonable_Pass1 <- Data_All_Reasonable %>% filter(q19 == 15)

# Print participant counts
condition_counts <- data.frame(
  Condition = c("Average", "Ideal", "Reasonable"),
  Original_Count = c(nrow(Data_All_Average), nrow(Data_All_Ideal), nrow(Data_All_Reasonable)),
  After_Attention_Check = c(nrow(Data_All_Average_Pass1), nrow(Data_All_Ideal_Pass1), nrow(Data_All_Reasonable_Pass1)),
  Excluded_Count = c(nrow(Data_All_Average) - nrow(Data_All_Average_Pass1),
                     nrow(Data_All_Ideal) - nrow(Data_All_Ideal_Pass1),
                     nrow(Data_All_Reasonable) - nrow(Data_All_Reasonable_Pass1)),
  Exclusion_Rate = c((nrow(Data_All_Average) - nrow(Data_All_Average_Pass1))/nrow(Data_All_Average),
                     (nrow(Data_All_Ideal) - nrow(Data_All_Ideal_Pass1))/nrow(Data_All_Ideal),
                     (nrow(Data_All_Reasonable) - nrow(Data_All_Reasonable_Pass1))/nrow(Data_All_Reasonable))
)

# Format the exclusion rate as percentage
condition_counts$Exclusion_Rate <- scales::percent(condition_counts$Exclusion_Rate)

# Display the participant counts table
kable(condition_counts, caption = "Participant Counts Before and After Attention Check") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

```{r}
# Define the question columns - ensuring they actually exist in the data
question_cols <- c("q1", "q2", "q3", "q4", "q5", "q6", "q7", "q8", "q9", "q10", 
                   "q11", "q12", "q13", "q14", "q15", "q16", "q17", "q18", 
                   "q20", "q21", "q22", "q23", "q24", "q25", "q26", "q27", 
                   "q28", "q29", "q30", "q31", "q32", "q33", "q34")

# Check if all question columns exist in the data
existing_cols <- question_cols[question_cols %in% colnames(Data_All_Average_Pass1)]
missing_cols <- question_cols[!question_cols %in% colnames(Data_All_Average_Pass1)]

print("Existing question columns:")
print(existing_cols)
print("Missing question columns:")
print(missing_cols)
```

#### 3. Check Number of Participants per Condition 

```{r}
# Continue with only the existing columns
question_cols <- existing_cols

# Convert columns to numeric
Data_All_Average_Pass1 <- Data_All_Average_Pass1 %>%
  mutate(across(all_of(question_cols), ~as.numeric(as.character(.))))

Data_All_Ideal_Pass1 <- Data_All_Ideal_Pass1 %>%
  mutate(across(all_of(question_cols), ~as.numeric(as.character(.))))

Data_All_Reasonable_Pass1 <- Data_All_Reasonable_Pass1 %>%
  mutate(across(all_of(question_cols), ~as.numeric(as.character(.))))

# Verify the number of participants in each condition
cat("Ideal condition:", nrow(Data_All_Ideal_Pass1), "participants\n")
cat("Average condition:", nrow(Data_All_Average_Pass1), "participants\n")
cat("Reasonable condition:", nrow(Data_All_Reasonable_Pass1), "participants\n")
```

#### 4a. Filter Data [Due to medians, exclusions of outliers]

No parts to be completed here: done in Analysis 3.

#### 4b. Filter Data [Any response that is > 3SD from QMean, exclude]

```{r}
# Function to filter data based on 3 SD criterion
filter_data <- function(data, cols) {
  # Pre-allocate a list to track excluded participants for each question
  exclusions_by_question <- list()
  
  # Original count
  original_count <- nrow(data)
  
  result <- data
  for (col in cols) {
    if (col %in% colnames(data)) {
      # Calculate mean and standard deviation
      avg <- mean(result[[col]], na.rm = TRUE)
      s <- sd(result[[col]], na.rm = TRUE)
      
      # Identify outliers
      outlier_indices <- which(!is.na(result[[col]]) & abs(result[[col]] - avg) > 3 * s)
      exclusions_by_question[[col]] <- length(outlier_indices)
      
      # Filter out outliers
      result <- result %>%
        filter(is.na(!!sym(col)) | abs(!!sym(col) - avg) <= 3 * s)
    }
  }
  
  # Final count
  final_count <- nrow(result)
  
  return(list(
    filtered_data = result,
    original_count = original_count,
    final_count = final_count,
    excluded_count = original_count - final_count,
    exclusion_rate = (original_count - final_count) / original_count,
    exclusions_by_question = exclusions_by_question
  ))
}

# Apply filtering and track exclusion counts
avg_filter_results <- filter_data(Data_All_Average_Pass1, question_cols)
ideal_filter_results <- filter_data(Data_All_Ideal_Pass1, question_cols)
reasonable_filter_results <- filter_data(Data_All_Reasonable_Pass1, question_cols)

# Extract the filtered data
Data_All_Average_Filtered <- avg_filter_results$filtered_data
Data_All_Ideal_Filtered <- ideal_filter_results$filtered_data
Data_All_Reasonable_Filtered <- reasonable_filter_results$filtered_data

# Display outlier exclusion summary
outlier_summary <- data.frame(
  Condition = c("Average", "Ideal", "Reasonable"),
  Original_Count = c(avg_filter_results$original_count, 
                     ideal_filter_results$original_count, 
                     reasonable_filter_results$original_count),
  After_Outlier_Removal = c(avg_filter_results$final_count, 
                            ideal_filter_results$final_count, 
                            reasonable_filter_results$final_count),
  Excluded_Count = c(avg_filter_results$excluded_count, 
                     ideal_filter_results$excluded_count, 
                     reasonable_filter_results$excluded_count),
  Exclusion_Rate = c(avg_filter_results$exclusion_rate,
                     ideal_filter_results$exclusion_rate,
                     reasonable_filter_results$exclusion_rate)
)

# Format the exclusion rate as percentage
outlier_summary$Exclusion_Rate <- scales::percent(outlier_summary$Exclusion_Rate)

# Display the outlier exclusion summary table
kable(outlier_summary, caption = "Participant Counts Before and After Outlier Removal") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

```{r}
# Helper functions
get_model_coefs <- function(model) {
  summary_model <- summary(model)
  coef_table <- summary_model$coefficients
  data.frame(
    Term = rownames(coef_table),
    Estimate = coef_table[, "Estimate"],
    Std_Error = coef_table[, "Std. Error"],
    t_value = coef_table[, "t value"],
    p_value = coef_table[, "Pr(>|t|)"]
  )
}

format_pvalue <- function(p_value) {
  if (is.na(p_value)) {
    return("NA")
  } else if (p_value < 0.001) {
    return("< .001")
  } else {
    formatted_p <- sprintf("%.3f", p_value)
    formatted_p <- sub("^0\\.", ".", formatted_p)
    if (formatted_p == "1.000" && p_value < 1) {
        return(".999")
    } else if (formatted_p == "1.000" && p_value >= 1) {
        return("1.000")
    }
    return(formatted_p)
  }
}

log_smallvalue <- function(x) {
  x_safe <- x
  x_safe[which(x == 0 & !is.na(x))] <- 0.01
  log(x_safe)
}

log_plus_one <- function(x) {
  log(x + 1)
}
```

# Analysis 3 [NO 3 SD Removed]: Overall results, with median ratings

#### 1. Compute the median rating

```{r}
# Calculate medians from attention-check filtered data ONLY
column_medians_average_no3sd <- sapply(Data_All_Average_Pass1[, question_cols], median, na.rm = TRUE)
column_medians_ideal_no3sd <- sapply(Data_All_Ideal_Pass1[, question_cols], median, na.rm = TRUE)
column_medians_reasonable_no3sd <- sapply(Data_All_Reasonable_Pass1[, question_cols], median, na.rm = TRUE)

# Create a dataframe for the medians (NO 3SD)
medians_df_no3sd <- data.frame(
  Question = names(column_medians_average_no3sd),
  Average = column_medians_average_no3sd,
  Ideal = column_medians_ideal_no3sd,
  Reasonable = column_medians_reasonable_no3sd
)

# Display the medians for each question
kable(medians_df_no3sd, caption = "Median Values (NO 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

#### 2a. (Small constant inf values): Convert median responses to a natural log scale (NO 3SD Removal)

```{r}
# Define Log function: Small constant for zero
log_smallvalue <- function(x) {
  x_safe <- x
  # Replace only actual zeros, leave NAs as NA
  x_safe[which(x == 0 & !is.na(x))] <- 0.01
  log(x_safe)
}

# Apply the log function to NO 3SD medians
log_medians_average_no3sd_smallval <- log_smallvalue(column_medians_average_no3sd)
log_medians_ideal_no3sd_smallval <- log_smallvalue(column_medians_ideal_no3sd)
log_medians_reasonable_no3sd_smallval <- log_smallvalue(column_medians_reasonable_no3sd)

# Create a dataframe for the log medians (NO 3SD, Small Constant)
log_medians_df_no3sd_smallval <- data.frame(
  Question = names(log_medians_average_no3sd_smallval),
  Average = log_medians_average_no3sd_smallval,
  Ideal = log_medians_ideal_no3sd_smallval,
  Reasonable = log_medians_reasonable_no3sd_smallval
)

# Display the log medians
kable(log_medians_df_no3sd_smallval, caption = "Log-Transformed (Small Constant) Median Values (NO 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

#### 2b. (Plus one to all values): Convert median responses to a natural log scale (NO 3SD Removal)

```{r}
# Define Log function: Add 1
log_plus_one <- function(x) {
  log(x + 1)
}

# Apply the log function to NO 3SD medians
log_medians_average_no3sd_plusone <- log_plus_one(column_medians_average_no3sd)
log_medians_ideal_no3sd_plusone <- log_plus_one(column_medians_ideal_no3sd)
log_medians_reasonable_no3sd_plusone <- log_plus_one(column_medians_reasonable_no3sd)

# Create a dataframe for the log medians (NO 3SD, Plus One)
log_medians_df_no3sd_plusone <- data.frame(
  Question = names(log_medians_average_no3sd_plusone),
  Average = log_medians_average_no3sd_plusone,
  Ideal = log_medians_ideal_no3sd_plusone,
  Reasonable = log_medians_reasonable_no3sd_plusone
)

# Display the log medians
kable(log_medians_df_no3sd_plusone, caption = "Log-Transformed (Plus One) Median Values (NO 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

#### 3a. (Small constant inf values): Conduct three regressions and record AIC (NO 3SD Removal)

```{r}
# Create data frame for regression (NO 3SD, Small Constant)
dataforAICMedians_no3sd_smallval <- data.frame(
  Reasonable = log_medians_reasonable_no3sd_smallval,
  Average = log_medians_average_no3sd_smallval,
  Ideal = log_medians_ideal_no3sd_smallval
)

# Filter out rows with non-finite values before regression
dataforAICMedians_no3sd_smallval_clean <- dataforAICMedians_no3sd_smallval %>%
  filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

# Check if enough data points remain
if(nrow(dataforAICMedians_no3sd_smallval_clean) > 3) {

  # Model I
  Model1Medians_no3sd_smallval <- lm(Reasonable ~ Average, data = dataforAICMedians_no3sd_smallval_clean)
  AIC1Medians_no3sd_smallval <- AIC(Model1Medians_no3sd_smallval)
  r2_model1_median_no3sd_smallval <- summary(Model1Medians_no3sd_smallval)$r.squared

  # Model II
  Model2Medians_no3sd_smallval <- lm(Reasonable ~ Ideal, data = dataforAICMedians_no3sd_smallval_clean)
  AIC2Medians_no3sd_smallval <- AIC(Model2Medians_no3sd_smallval)
  r2_model2_median_no3sd_smallval <- summary(Model2Medians_no3sd_smallval)$r.squared

  # Model III
  Model3Medians_no3sd_smallval <- lm(Reasonable ~ Average + Ideal, data = dataforAICMedians_no3sd_smallval_clean)
  AIC3Medians_no3sd_smallval <- AIC(Model3Medians_no3sd_smallval)
  r2_model3_median_no3sd_smallval <- summary(Model3Medians_no3sd_smallval)$r.squared

  # Create a regression summary dataframe
  regression_summary_medians_no3sd_smallval <- data.frame(
    Model = c("Average predicts Reasonable",
              "Ideal predicts Reasonable",
              "Average + Ideal predict Reasonable"),
    AIC = c(AIC1Medians_no3sd_smallval, AIC2Medians_no3sd_smallval, AIC3Medians_no3sd_smallval),
    R_squared = c(r2_model1_median_no3sd_smallval, r2_model2_median_no3sd_smallval, r2_model3_median_no3sd_smallval)
  )

  # Display the regression summary table
  kable(regression_summary_medians_no3sd_smallval, caption = "Regression Comparison (Median, NO 3SD, Log Small Constant)") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

} else {
  cat("Not enough valid data points for regression (NO 3SD, Log Small Constant).\n")
  regression_summary_medians_no3sd_smallval <- data.frame(Model=character(), AIC=numeric(), R_squared=numeric())
}
```

#### 3b. (Plus one to all values): Conduct three regressions and record AIC (NO 3SD Removal)

```{r}
# Create data frame for regression (NO 3SD, Plus One)
dataforAICMedians_no3sd_plusone <- data.frame(
  Reasonable = log_medians_reasonable_no3sd_plusone,
  Average = log_medians_average_no3sd_plusone,
  Ideal = log_medians_ideal_no3sd_plusone
)

# Filter out rows with non-finite values before regression
dataforAICMedians_no3sd_plusone_clean <- dataforAICMedians_no3sd_plusone %>%
  filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

# Check if enough data points remain
if(nrow(dataforAICMedians_no3sd_plusone_clean) > 3) {

  # Model I
  Model1Medians_no3sd_plusone <- lm(Reasonable ~ Average, data = dataforAICMedians_no3sd_plusone_clean)
  AIC1Medians_no3sd_plusone <- AIC(Model1Medians_no3sd_plusone)
  r2_model1_median_no3sd_plusone <- summary(Model1Medians_no3sd_plusone)$r.squared

  # Model II
  Model2Medians_no3sd_plusone <- lm(Reasonable ~ Ideal, data = dataforAICMedians_no3sd_plusone_clean)
  AIC2Medians_no3sd_plusone <- AIC(Model2Medians_no3sd_plusone)
  r2_model2_median_no3sd_plusone <- summary(Model2Medians_no3sd_plusone)$r.squared

  # Model III
  Model3Medians_no3sd_plusone <- lm(Reasonable ~ Average + Ideal, data = dataforAICMedians_no3sd_plusone_clean)
  AIC3Medians_no3sd_plusone <- AIC(Model3Medians_no3sd_plusone)
  r2_model3_median_no3sd_plusone <- summary(Model3Medians_no3sd_plusone)$r.squared

  # Create a regression summary dataframe
  regression_summary_medians_no3sd_plusone <- data.frame(
    Model = c("Average predicts Reasonable",
              "Ideal predicts Reasonable",
              "Average + Ideal predict Reasonable"),
    AIC = c(AIC1Medians_no3sd_plusone, AIC2Medians_no3sd_plusone, AIC3Medians_no3sd_plusone),
    R_squared = c(r2_model1_median_no3sd_plusone, r2_model2_median_no3sd_plusone, r2_model3_median_no3sd_plusone)
  )

  # Display the regression summary table
  kable(regression_summary_medians_no3sd_plusone, caption = "Regression Comparison (Median, NO 3SD, Log Plus One)") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

} else {
   cat("Not enough valid data points for regression (NO 3SD, Log Plus One).\n")
   regression_summary_medians_no3sd_plusone <- data.frame(Model=character(), AIC=numeric(), R_squared=numeric())
}
```

#### 4a. (Small constant inf values): Plots and Reporting (NO 3SD Removal)

```{r}
# Check if models exist before plotting
if(exists("Model1Medians_no3sd_smallval") && exists("dataforAICMedians_no3sd_smallval_clean") && nrow(dataforAICMedians_no3sd_smallval_clean) > 0) {

  # Average Median vs Reasonable Median
  plot1_median_no3sd_smallval <- ggplot(dataforAICMedians_no3sd_smallval_clean, aes(x = Average, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "blue") +
    labs(title = "Model 1 (NO 3SD, Log Small Const): Median Average vs Reasonable",
         subtitle = paste("AIC =", round(AIC1Medians_no3sd_smallval, 2), ", R² =", round(r2_model1_median_no3sd_smallval, 3)),
         x = "Log (Small Const) Median Average Rating", y = "Log (Small Const) Median Reasonable Rating") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Ideal Median vs Reasonable Median
  plot2_median_no3sd_smallval <- ggplot(dataforAICMedians_no3sd_smallval_clean, aes(x = Ideal, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "red") +
    labs(title = "Model 2 (NO 3SD, Log Small Const): Median Ideal vs Reasonable",
         subtitle = paste("AIC =", round(AIC2Medians_no3sd_smallval, 2), ", R² =", round(r2_model2_median_no3sd_smallval, 3)),
         x = "Log (Small Const) Median Ideal Rating", y = "Log (Small Const) Median Reasonable Rating") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Average effect)
  new_data_median_no3sd_smallval <- expand.grid( Average = seq(min(dataforAICMedians_no3sd_smallval_clean$Average, na.rm=TRUE), max(dataforAICMedians_no3sd_smallval_clean$Average, na.rm=TRUE), length.out = 100), Ideal = median(dataforAICMedians_no3sd_smallval_clean$Ideal, na.rm=TRUE) )
  new_data_median_no3sd_smallval <- new_data_median_no3sd_smallval[is.finite(new_data_median_no3sd_smallval$Average) & is.finite(new_data_median_no3sd_smallval$Ideal),]
  if(nrow(new_data_median_no3sd_smallval)>0){ new_data_median_no3sd_smallval$predicted_reasonable <- predict(Model3Medians_no3sd_smallval, newdata = new_data_median_no3sd_smallval) } else { new_data_median_no3sd_smallval <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric())}
  plot3_median_no3sd_smallval <- ggplot(dataforAICMedians_no3sd_smallval_clean, aes(x = Average, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data_median_no3sd_smallval, aes(y = predicted_reasonable), color = "blue", size = 1) + labs(title = "Model 3 (NO 3SD, Log Small Const): Effect of Median Average", subtitle = paste("AIC =", round(AIC3Medians_no3sd_smallval, 2), ", R² =", round(r2_model3_median_no3sd_smallval, 3)), x = "Log (Small Const) Median Average Rating", y = "Log (Small Const) Median Reasonable Rating") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Ideal effect)
  new_data2_median_no3sd_smallval <- expand.grid( Average = median(dataforAICMedians_no3sd_smallval_clean$Average, na.rm=TRUE), Ideal = seq(min(dataforAICMedians_no3sd_smallval_clean$Ideal, na.rm=TRUE), max(dataforAICMedians_no3sd_smallval_clean$Ideal, na.rm=TRUE), length.out = 100) )
  new_data2_median_no3sd_smallval <- new_data2_median_no3sd_smallval[is.finite(new_data2_median_no3sd_smallval$Average) & is.finite(new_data2_median_no3sd_smallval$Ideal),]
  if(nrow(new_data2_median_no3sd_smallval)>0){ new_data2_median_no3sd_smallval$predicted_reasonable <- predict(Model3Medians_no3sd_smallval, newdata = new_data2_median_no3sd_smallval) } else { new_data2_median_no3sd_smallval <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric())}
  plot4_median_no3sd_smallval <- ggplot(dataforAICMedians_no3sd_smallval_clean, aes(x = Ideal, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data2_median_no3sd_smallval, aes(y = predicted_reasonable), color = "red", size = 1) + labs(title = "Model 3 (NO 3SD, Log Small Const): Effect of Median Ideal", subtitle = paste("AIC =", round(AIC3Medians_no3sd_smallval, 2), ", R² =", round(r2_model3_median_no3sd_smallval, 3)), x = "Log (Small Const) Median Ideal Rating", y = "Log (Small Const) Median Reasonable Rating") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Display plots
  print(plot1_median_no3sd_smallval)
  print(plot2_median_no3sd_smallval)
  print(plot3_median_no3sd_smallval)
  print(plot4_median_no3sd_smallval)

  # Save plots
  ggsave("model1_median_avg_reas_no3sd_smallval.png", plot1_median_no3sd_smallval, width = 8, height = 6, dpi = 300)
  ggsave("model2_median_ideal_reas_no3sd_smallval.png", plot2_median_no3sd_smallval, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_avg_eff_no3sd_smallval.png", plot3_median_no3sd_smallval, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_ideal_eff_no3sd_smallval.png", plot4_median_no3sd_smallval, width = 8, height = 6, dpi = 300)
  grid_plots_median_no3sd_smallval <- grid.arrange(plot1_median_no3sd_smallval, plot2_median_no3sd_smallval, plot3_median_no3sd_smallval, plot4_median_no3sd_smallval, ncol = 2)
  ggsave("all_median_plots_no3sd_smallval.png", grid_plots_median_no3sd_smallval, width = 14, height = 10, dpi = 300)

  # Correlation matrix
  cor_data_no3sd_smallval <- dataforAICMedians_no3sd_smallval_clean[complete.cases(dataforAICMedians_no3sd_smallval_clean),]
  if(nrow(cor_data_no3sd_smallval) > 1) {
   cor_matrix_no3sd_smallval <- cor(cor_data_no3sd_smallval, use = "complete.obs")
   corrplot(cor_matrix_no3sd_smallval, method = "color", type = "upper", addCoef.col = "black", tl.col = "black", tl.srt = 45, diag = FALSE, title = "Correlation Matrix (NO 3SD, Log Small Constant)", mar = c(0,0,1,0))
  } else { cat("Not enough data for correlation matrix (NO 3SD, Log Small Constant).\n") }

  # Coefficient tables
  model1_coefs_no3sd_smallval <- get_model_coefs(Model1Medians_no3sd_smallval)
  model2_coefs_no3sd_smallval <- get_model_coefs(Model2Medians_no3sd_smallval)
  model3_coefs_no3sd_smallval <- get_model_coefs(Model3Medians_no3sd_smallval)
  model1_coefs_no3sd_smallval$p_value <- sapply(model1_coefs_no3sd_smallval$p_value, format_pvalue)
  model2_coefs_no3sd_smallval$p_value <- sapply(model2_coefs_no3sd_smallval$p_value, format_pvalue)
  model3_coefs_no3sd_smallval$p_value <- sapply(model3_coefs_no3sd_smallval$p_value, format_pvalue)
  kable(model1_coefs_no3sd_smallval, caption = "Model 1 Coeffs (NO 3SD, Log Small Const)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model2_coefs_no3sd_smallval, caption = "Model 2 Coeffs (NO 3SD, Log Small Const)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model3_coefs_no3sd_smallval, caption = "Model 3 Coeffs (NO 3SD, Log Small Const)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

  # Print model summaries
  cat("\nModel Summaries (NO 3SD, Log Small Constant):\n")
  print(summary(Model1Medians_no3sd_smallval))
  print(summary(Model2Medians_no3sd_smallval))
  print(summary(Model3Medians_no3sd_smallval))

} else {
   cat("Skipping plots and summaries for (NO 3SD, Log Small Constant) due to insufficient data.\n")
}

# Store results
analysis_3_results_no3sd_smallval <- list(
  medians_by_question = if(exists("medians_df_no3sd")) medians_df_no3sd else NULL,
  log_medians_by_question = if(exists("log_medians_df_no3sd_smallval")) log_medians_df_no3sd_smallval else NULL,
  regression_models = if(exists("Model1Medians_no3sd_smallval")) list(model1 = Model1Medians_no3sd_smallval, model2 = Model2Medians_no3sd_smallval, model3 = Model3Medians_no3sd_smallval) else NULL,
  regression_summary = if(exists("regression_summary_medians_no3sd_smallval")) regression_summary_medians_no3sd_smallval else NULL,
  aic_values = if(exists("AIC1Medians_no3sd_smallval")) c(AIC1 = AIC1Medians_no3sd_smallval, AIC2 = AIC2Medians_no3sd_smallval, AIC3 = AIC3Medians_no3sd_smallval) else NULL
)
```
#### 4b. (Plus one to all values): Plots and Reporting (NO 3SD Removal)

```{r}
# Check if models exist before plotting
if(exists("Model1Medians_no3sd_plusone") && exists("dataforAICMedians_no3sd_plusone_clean") && nrow(dataforAICMedians_no3sd_plusone_clean) > 0) {

  # Average Median vs Reasonable Median
  plot1_median_no3sd_plusone <- ggplot(dataforAICMedians_no3sd_plusone_clean, aes(x = Average, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "blue") +
    labs(title = "Model 1 (NO 3SD, Log+1): Median Average vs Reasonable",
         subtitle = paste("AIC =", round(AIC1Medians_no3sd_plusone, 2), ", R² =", round(r2_model1_median_no3sd_plusone, 3)),
         x = "Log (+1) Median Average Rating", y = "Log (+1) Median Reasonable Rating") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Ideal Median vs Reasonable Median
  plot2_median_no3sd_plusone <- ggplot(dataforAICMedians_no3sd_plusone_clean, aes(x = Ideal, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "red") +
    labs(title = "Model 2 (NO 3SD, Log+1): Median Ideal vs Reasonable",
         subtitle = paste("AIC =", round(AIC2Medians_no3sd_plusone, 2), ", R² =", round(r2_model2_median_no3sd_plusone, 3)),
         x = "Log (+1) Median Ideal Rating", y = "Log (+1) Median Reasonable Rating") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Average effect)
  new_data_median_no3sd_plusone <- expand.grid( Average = seq(min(dataforAICMedians_no3sd_plusone_clean$Average, na.rm=TRUE), max(dataforAICMedians_no3sd_plusone_clean$Average, na.rm=TRUE), length.out = 100), Ideal = median(dataforAICMedians_no3sd_plusone_clean$Ideal, na.rm=TRUE) )
  new_data_median_no3sd_plusone <- new_data_median_no3sd_plusone[is.finite(new_data_median_no3sd_plusone$Average) & is.finite(new_data_median_no3sd_plusone$Ideal),]
  if(nrow(new_data_median_no3sd_plusone)>0){ new_data_median_no3sd_plusone$predicted_reasonable <- predict(Model3Medians_no3sd_plusone, newdata = new_data_median_no3sd_plusone) } else { new_data_median_no3sd_plusone <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric())}
  plot3_median_no3sd_plusone <- ggplot(dataforAICMedians_no3sd_plusone_clean, aes(x = Average, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data_median_no3sd_plusone, aes(y = predicted_reasonable), color = "blue", size = 1) + labs(title = "Model 3 (NO 3SD, Log+1): Effect of Median Average", subtitle = paste("AIC =", round(AIC3Medians_no3sd_plusone, 2), ", R² =", round(r2_model3_median_no3sd_plusone, 3)), x = "Log (+1) Median Average Rating", y = "Log (+1) Median Reasonable Rating") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Ideal effect)
  new_data2_median_no3sd_plusone <- expand.grid( Average = median(dataforAICMedians_no3sd_plusone_clean$Average, na.rm=TRUE), Ideal = seq(min(dataforAICMedians_no3sd_plusone_clean$Ideal, na.rm=TRUE), max(dataforAICMedians_no3sd_plusone_clean$Ideal, na.rm=TRUE), length.out = 100) )
  new_data2_median_no3sd_plusone <- new_data2_median_no3sd_plusone[is.finite(new_data2_median_no3sd_plusone$Average) & is.finite(new_data2_median_no3sd_plusone$Ideal),]
  if(nrow(new_data2_median_no3sd_plusone)>0){ new_data2_median_no3sd_plusone$predicted_reasonable <- predict(Model3Medians_no3sd_plusone, newdata = new_data2_median_no3sd_plusone) } else { new_data2_median_no3sd_plusone <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric())}
  plot4_median_no3sd_plusone <- ggplot(dataforAICMedians_no3sd_plusone_clean, aes(x = Ideal, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data2_median_no3sd_plusone, aes(y = predicted_reasonable), color = "red", size = 1) + labs(title = "Model 3 (NO 3SD, Log+1): Effect of Median Ideal", subtitle = paste("AIC =", round(AIC3Medians_no3sd_plusone, 2), ", R² =", round(r2_model3_median_no3sd_plusone, 3)), x = "Log (+1) Median Ideal Rating", y = "Log (+1) Median Reasonable Rating") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Display plots
  print(plot1_median_no3sd_plusone)
  print(plot2_median_no3sd_plusone)
  print(plot3_median_no3sd_plusone)
  print(plot4_median_no3sd_plusone)

  # Save plots
  ggsave("model1_median_avg_reas_no3sd_plusone.png", plot1_median_no3sd_plusone, width = 8, height = 6, dpi = 300)
  ggsave("model2_median_ideal_reas_no3sd_plusone.png", plot2_median_no3sd_plusone, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_avg_eff_no3sd_plusone.png", plot3_median_no3sd_plusone, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_ideal_eff_no3sd_plusone.png", plot4_median_no3sd_plusone, width = 8, height = 6, dpi = 300)
  grid_plots_median_no3sd_plusone <- grid.arrange(plot1_median_no3sd_plusone, plot2_median_no3sd_plusone, plot3_median_no3sd_plusone, plot4_median_no3sd_plusone, ncol = 2)
  ggsave("all_median_plots_no3sd_plusone.png", grid_plots_median_no3sd_plusone, width = 14, height = 10, dpi = 300)

  # Correlation matrix
  cor_data_no3sd_plusone <- dataforAICMedians_no3sd_plusone_clean[complete.cases(dataforAICMedians_no3sd_plusone_clean),]
  if(nrow(cor_data_no3sd_plusone) > 1) {
   cor_matrix_no3sd_plusone <- cor(cor_data_no3sd_plusone, use = "complete.obs")
   corrplot(cor_matrix_no3sd_plusone, method = "color", type = "upper", addCoef.col = "black", tl.col = "black", tl.srt = 45, diag = FALSE, title = "Correlation Matrix (NO 3SD, Log Plus One)", mar = c(0,0,1,0))
  } else { cat("Not enough data for correlation matrix (NO 3SD, Log Plus One).\n") }

  # Coefficient tables
  model1_coefs_no3sd_plusone <- get_model_coefs(Model1Medians_no3sd_plusone)
  model2_coefs_no3sd_plusone <- get_model_coefs(Model2Medians_no3sd_plusone)
  model3_coefs_no3sd_plusone <- get_model_coefs(Model3Medians_no3sd_plusone)
  model1_coefs_no3sd_plusone$p_value <- sapply(model1_coefs_no3sd_plusone$p_value, format_pvalue)
  model2_coefs_no3sd_plusone$p_value <- sapply(model2_coefs_no3sd_plusone$p_value, format_pvalue)
  model3_coefs_no3sd_plusone$p_value <- sapply(model3_coefs_no3sd_plusone$p_value, format_pvalue)
  kable(model1_coefs_no3sd_plusone, caption = "Model 1 Coeffs (NO 3SD, Log Plus One)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model2_coefs_no3sd_plusone, caption = "Model 2 Coeffs (NO 3SD, Log Plus One)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model3_coefs_no3sd_plusone, caption = "Model 3 Coeffs (NO 3SD, Log Plus One)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

  # Print model summaries
  cat("\nModel Summaries (NO 3SD, Log Plus One):\n")
  print(summary(Model1Medians_no3sd_plusone))
  print(summary(Model2Medians_no3sd_plusone))
  print(summary(Model3Medians_no3sd_plusone))

} else {
  cat("Skipping plots and summaries for (NO 3SD, Log Plus One) due to insufficient data.\n")
}

# Store results
analysis_3_results_no3sd_plusone <- list(
  medians_by_question = if(exists("medians_df_no3sd")) medians_df_no3sd else NULL,
  log_medians_by_question = if(exists("log_medians_df_no3sd_plusone")) log_medians_df_no3sd_plusone else NULL,
  regression_models = if(exists("Model1Medians_no3sd_plusone")) list(model1 = Model1Medians_no3sd_plusone, model2 = Model2Medians_no3sd_plusone, model3 = Model3Medians_no3sd_plusone) else NULL,
  regression_summary = if(exists("regression_summary_medians_no3sd_plusone")) regression_summary_medians_no3sd_plusone else NULL,
  aic_values = if(exists("AIC1Medians_no3sd_plusone")) c(AIC1 = AIC1Medians_no3sd_plusone, AIC2 = AIC2Medians_no3sd_plusone, AIC3 = AIC3Medians_no3sd_plusone) else NULL
)
```

# Analysis 3 [WITH 3 SD removed]: Overall results, with median ratings

#### 1. Compute the median rating 

```{r}
# Calculate medians from data filtered for attention check AND 3SD outliers
column_medians_average_3sd <- sapply(Data_All_Average_Filtered[, question_cols], median, na.rm = TRUE)
column_medians_ideal_3sd <- sapply(Data_All_Ideal_Filtered[, question_cols], median, na.rm = TRUE)
column_medians_reasonable_3sd <- sapply(Data_All_Reasonable_Filtered[, question_cols], median, na.rm = TRUE)

# Create a dataframe for the medians (WITH 3SD)
medians_df_3sd <- data.frame(
  Question = names(column_medians_average_3sd),
  Average = column_medians_average_3sd,
  Ideal = column_medians_ideal_3sd,
  Reasonable = column_medians_reasonable_3sd
)

# Display the medians for each question
kable(medians_df_3sd, caption = "Median Values (WITH 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

#### 2a. (Small constant inf values): Convert median responses to a natural log scale (WITH 3SD Removal)

```{r}
# Define Log function: Small constant for zero
log_smallvalue <- function(x) {
  x_safe <- x
  # Replace only actual zeros, leave NAs as NA
  x_safe[which(x == 0 & !is.na(x))] <- 0.01
  log(x_safe)
}

# Apply the log function: log_smallvalue (defined earlier)
log_medians_average_3sd_smallval <- log_smallvalue(column_medians_average_3sd)
log_medians_ideal_3sd_smallval <- log_smallvalue(column_medians_ideal_3sd)
log_medians_reasonable_3sd_smallval <- log_smallvalue(column_medians_reasonable_3sd)

# Create a dataframe for the log medians (WITH 3SD, Small Constant)
log_medians_df_3sd_smallval <- data.frame(
  Question = names(log_medians_average_3sd_smallval),
  Average = log_medians_average_3sd_smallval,
  Ideal = log_medians_ideal_3sd_smallval,
  Reasonable = log_medians_reasonable_3sd_smallval
)

# Display the log medians
kable(log_medians_df_3sd_smallval, caption = "Log-Transformed (Small Constant) Median Values (WITH 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

#### 2b. (Plus one to all values): Convert median responses to a natural log scale (WITH 3SD Removal)

```{r}
# Define Log function: Add 1
log_plus_one <- function(x) {
  log(x + 1)
}

# Apply the log function: log_plus_one (defined earlier)
log_medians_average_3sd_plusone <- log_plus_one(column_medians_average_3sd)
log_medians_ideal_3sd_plusone <- log_plus_one(column_medians_ideal_3sd)
log_medians_reasonable_3sd_plusone <- log_plus_one(column_medians_reasonable_3sd)

# Create a dataframe for the log medians (WITH 3SD, Plus One)
log_medians_df_3sd_plusone <- data.frame(
  Question = names(log_medians_average_3sd_plusone),
  Average = log_medians_average_3sd_plusone,
  Ideal = log_medians_ideal_3sd_plusone,
  Reasonable = log_medians_reasonable_3sd_plusone
)

# Display the log medians
kable(log_medians_df_3sd_plusone, caption = "Log-Transformed (Plus One) Median Values (WITH 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

#### 3a. (Small constant inf values): Conduct three regressions and record AIC (WITH 3SD Removal)

```{r}
# Create data frame for regression (WITH 3SD, Small Constant)
dataforAICMedians_3sd_smallval <- data.frame(
  Reasonable = log_medians_reasonable_3sd_smallval,
  Average = log_medians_average_3sd_smallval,
  Ideal = log_medians_ideal_3sd_smallval
)

# Filter out rows with non-finite values before regression
dataforAICMedians_3sd_smallval_clean <- dataforAICMedians_3sd_smallval %>%
  filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

# Check if enough data points remain
if(nrow(dataforAICMedians_3sd_smallval_clean) > 3) {

  # Model I
  Model1Medians_3sd_smallval <- lm(Reasonable ~ Average, data = dataforAICMedians_3sd_smallval_clean)
  AIC1Medians_3sd_smallval <- AIC(Model1Medians_3sd_smallval)
  r2_model1_median_3sd_smallval <- summary(Model1Medians_3sd_smallval)$r.squared

  # Model II
  Model2Medians_3sd_smallval <- lm(Reasonable ~ Ideal, data = dataforAICMedians_3sd_smallval_clean)
  AIC2Medians_3sd_smallval <- AIC(Model2Medians_3sd_smallval)
  r2_model2_median_3sd_smallval <- summary(Model2Medians_3sd_smallval)$r.squared

  # Model III
  Model3Medians_3sd_smallval <- lm(Reasonable ~ Average + Ideal, data = dataforAICMedians_3sd_smallval_clean)
  AIC3Medians_3sd_smallval <- AIC(Model3Medians_3sd_smallval)
  r2_model3_median_3sd_smallval <- summary(Model3Medians_3sd_smallval)$r.squared

  # Create a regression summary dataframe
  regression_summary_medians_3sd_smallval <- data.frame(
    Model = c("Average predicts Reasonable",
              "Ideal predicts Reasonable",
              "Average + Ideal predict Reasonable"),
    AIC = c(AIC1Medians_3sd_smallval, AIC2Medians_3sd_smallval, AIC3Medians_3sd_smallval),
    R_squared = c(r2_model1_median_3sd_smallval, r2_model2_median_3sd_smallval, r2_model3_median_3sd_smallval)
  )

  # Display the regression summary table
  kable(regression_summary_medians_3sd_smallval, caption = "Regression Comparison (Median, WITH 3SD, Log Small Constant)") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

} else {
   cat("Not enough valid data points for regression (WITH 3SD, Log Small Constant).\n")
   regression_summary_medians_3sd_smallval <- data.frame(Model=character(), AIC=numeric(), R_squared=numeric())
}
```

#### 3b. (Plus one to all values): Conduct three regressions and record AIC (WITH 3SD Removal)

```{r}
# Create data frame for regression (WITH 3SD, Plus One)
dataforAICMedians_3sd_plusone <- data.frame(
  Reasonable = log_medians_reasonable_3sd_plusone,
  Average = log_medians_average_3sd_plusone,
  Ideal = log_medians_ideal_3sd_plusone
)

# Filter out rows with non-finite values before regression
dataforAICMedians_3sd_plusone_clean <- dataforAICMedians_3sd_plusone %>%
  filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

# Check if enough data points remain
if(nrow(dataforAICMedians_3sd_plusone_clean) > 3) {

  # Model I
  Model1Medians_3sd_plusone <- lm(Reasonable ~ Average, data = dataforAICMedians_3sd_plusone_clean)
  AIC1Medians_3sd_plusone <- AIC(Model1Medians_3sd_plusone)
  r2_model1_median_3sd_plusone <- summary(Model1Medians_3sd_plusone)$r.squared

  # Model II
  Model2Medians_3sd_plusone <- lm(Reasonable ~ Ideal, data = dataforAICMedians_3sd_plusone_clean)
  AIC2Medians_3sd_plusone <- AIC(Model2Medians_3sd_plusone)
  r2_model2_median_3sd_plusone <- summary(Model2Medians_3sd_plusone)$r.squared

  # Model III
  Model3Medians_3sd_plusone <- lm(Reasonable ~ Average + Ideal, data = dataforAICMedians_3sd_plusone_clean)
  AIC3Medians_3sd_plusone <- AIC(Model3Medians_3sd_plusone)
  r2_model3_median_3sd_plusone <- summary(Model3Medians_3sd_plusone)$r.squared

  # Create a regression summary dataframe
  regression_summary_medians_3sd_plusone <- data.frame(
    Model = c("Average predicts Reasonable",
              "Ideal predicts Reasonable",
              "Average + Ideal predict Reasonable"),
    AIC = c(AIC1Medians_3sd_plusone, AIC2Medians_3sd_plusone, AIC3Medians_3sd_plusone),
    R_squared = c(r2_model1_median_3sd_plusone, r2_model2_median_3sd_plusone, r2_model3_median_3sd_plusone)
  )

  # Display the regression summary table
  kable(regression_summary_medians_3sd_plusone, caption = "Regression Comparison (Median, WITH 3SD, Log Plus One)") %>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

} else {
  cat("Not enough valid data points for regression (WITH 3SD, Log Plus One).\n")
  regression_summary_medians_3sd_plusone <- data.frame(Model=character(), AIC=numeric(), R_squared=numeric())
}
```

#### 4a. (Small constant inf values): Plots and Reporting (WITH 3SD Removal)

```{r}
# Check if models exist before plotting
if(exists("Model1Medians_3sd_smallval") && exists("dataforAICMedians_3sd_smallval_clean") && nrow(dataforAICMedians_3sd_smallval_clean) > 0) {

  # Average Median vs Reasonable Median
  plot1_median_3sd_smallval <- ggplot(dataforAICMedians_3sd_smallval_clean, aes(x = Average, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "blue") +
    labs(title = "Model 1 (WITH 3SD, Log Small Const): Median Average vs Reasonable",
         subtitle = paste("AIC =", round(AIC1Medians_3sd_smallval, 2), ", R² =", round(r2_model1_median_3sd_smallval, 3)),
         x = "Log (Small Const) Median Average Rating (3SD Removed)",
         y = "Log (Small Const) Median Reasonable Rating (3SD Removed)") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Ideal Median vs Reasonable Median
  plot2_median_3sd_smallval <- ggplot(dataforAICMedians_3sd_smallval_clean, aes(x = Ideal, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "red") +
    labs(title = "Model 2 (WITH 3SD, Log Small Const): Median Ideal vs Reasonable",
         subtitle = paste("AIC =", round(AIC2Medians_3sd_smallval, 2), ", R² =", round(r2_model2_median_3sd_smallval, 3)),
         x = "Log (Small Const) Median Ideal Rating (3SD Removed)",
         y = "Log (Small Const) Median Reasonable Rating (3SD Removed)") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Average effect)
  new_data_median_3sd_smallval <- expand.grid( Average = seq(min(dataforAICMedians_3sd_smallval_clean$Average, na.rm=TRUE), max(dataforAICMedians_3sd_smallval_clean$Average, na.rm=TRUE), length.out = 100), Ideal = median(dataforAICMedians_3sd_smallval_clean$Ideal, na.rm=TRUE) )
  new_data_median_3sd_smallval <- new_data_median_3sd_smallval[is.finite(new_data_median_3sd_smallval$Average) & is.finite(new_data_median_3sd_smallval$Ideal),]
  if(nrow(new_data_median_3sd_smallval)>0){ new_data_median_3sd_smallval$predicted_reasonable <- predict(Model3Medians_3sd_smallval, newdata = new_data_median_3sd_smallval) } else { new_data_median_3sd_smallval <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric()) }
  plot3_median_3sd_smallval <- ggplot(dataforAICMedians_3sd_smallval_clean, aes(x = Average, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data_median_3sd_smallval, aes(y = predicted_reasonable), color = "blue", size = 1) + labs(title = "Model 3 (WITH 3SD, Log Small Const): Effect of Median Average", subtitle = paste("AIC =", round(AIC3Medians_3sd_smallval, 2), ", R² =", round(r2_model3_median_3sd_smallval, 3)), x = "Log (Small Const) Median Average Rating (3SD Removed)", y = "Log (Small Const) Median Reasonable Rating (3SD Removed)") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Ideal effect)
  new_data2_median_3sd_smallval <- expand.grid( Average = median(dataforAICMedians_3sd_smallval_clean$Average, na.rm=TRUE), Ideal = seq(min(dataforAICMedians_3sd_smallval_clean$Ideal, na.rm=TRUE), max(dataforAICMedians_3sd_smallval_clean$Ideal, na.rm=TRUE), length.out = 100) )
  new_data2_median_3sd_smallval <- new_data2_median_3sd_smallval[is.finite(new_data2_median_3sd_smallval$Average) & is.finite(new_data2_median_3sd_smallval$Ideal),]
  if(nrow(new_data2_median_3sd_smallval)>0){ new_data2_median_3sd_smallval$predicted_reasonable <- predict(Model3Medians_3sd_smallval, newdata = new_data2_median_3sd_smallval) } else { new_data2_median_3sd_smallval <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric()) }
  plot4_median_3sd_smallval <- ggplot(dataforAICMedians_3sd_smallval_clean, aes(x = Ideal, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data2_median_3sd_smallval, aes(y = predicted_reasonable), color = "red", size = 1) + labs(title = "Model 3 (WITH 3SD, Log Small Const): Effect of Median Ideal", subtitle = paste("AIC =", round(AIC3Medians_3sd_smallval, 2), ", R² =", round(r2_model3_median_3sd_smallval, 3)), x = "Log (Small Const) Median Ideal Rating (3SD Removed)", y = "Log (Small Const) Median Reasonable Rating (3SD Removed)") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Display plots
  print(plot1_median_3sd_smallval)
  print(plot2_median_3sd_smallval)
  print(plot3_median_3sd_smallval)
  print(plot4_median_3sd_smallval)

  # Save plots
  ggsave("model1_median_avg_reas_3sd_smallval.png", plot1_median_3sd_smallval, width = 8, height = 6, dpi = 300)
  ggsave("model2_median_ideal_reas_3sd_smallval.png", plot2_median_3sd_smallval, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_avg_eff_3sd_smallval.png", plot3_median_3sd_smallval, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_ideal_eff_3sd_smallval.png", plot4_median_3sd_smallval, width = 8, height = 6, dpi = 300)
  grid_plots_median_3sd_smallval <- grid.arrange(plot1_median_3sd_smallval, plot2_median_3sd_smallval, plot3_median_3sd_smallval, plot4_median_3sd_smallval, ncol = 2)
  ggsave("all_median_plots_3sd_smallval.png", grid_plots_median_3sd_smallval, width = 14, height = 10, dpi = 300)

  # Correlation matrix
  cor_data_3sd_smallval <- dataforAICMedians_3sd_smallval_clean[complete.cases(dataforAICMedians_3sd_smallval_clean),]
  if(nrow(cor_data_3sd_smallval) > 1) {
   cor_matrix_3sd_smallval <- cor(cor_data_3sd_smallval, use = "complete.obs")
   corrplot(cor_matrix_3sd_smallval, method = "color", type = "upper", addCoef.col = "black", tl.col = "black", tl.srt = 45, diag = FALSE, title = "Correlation Matrix (WITH 3SD, Log Small Constant)", mar = c(0,0,1,0))
  } else { cat("Not enough data for correlation matrix (WITH 3SD, Log Small Constant).\n") }

  # Coefficient tables
  model1_coefs_3sd_smallval <- get_model_coefs(Model1Medians_3sd_smallval)
  model2_coefs_3sd_smallval <- get_model_coefs(Model2Medians_3sd_smallval)
  model3_coefs_3sd_smallval <- get_model_coefs(Model3Medians_3sd_smallval)
  model1_coefs_3sd_smallval$p_value <- sapply(model1_coefs_3sd_smallval$p_value, format_pvalue)
  model2_coefs_3sd_smallval$p_value <- sapply(model2_coefs_3sd_smallval$p_value, format_pvalue)
  model3_coefs_3sd_smallval$p_value <- sapply(model3_coefs_3sd_smallval$p_value, format_pvalue)
  kable(model1_coefs_3sd_smallval, caption = "Model 1 Coeffs (WITH 3SD, Log Small Const)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model2_coefs_3sd_smallval, caption = "Model 2 Coeffs (WITH 3SD, Log Small Const)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model3_coefs_3sd_smallval, caption = "Model 3 Coeffs (WITH 3SD, Log Small Const)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

  # Print model summaries
  cat("\nModel Summaries (WITH 3SD, Log Small Constant):\n")
  print(summary(Model1Medians_3sd_smallval))
  print(summary(Model2Medians_3sd_smallval))
  print(summary(Model3Medians_3sd_smallval))

} else {
   cat("Skipping plots and summaries for (WITH 3SD, Log Small Constant) due to insufficient data.\n")
}

# Store results
analysis_3_results_3sd_smallval <- list(
  medians_by_question = if(exists("medians_df_3sd")) medians_df_3sd else NULL,
  log_medians_by_question = if(exists("log_medians_df_3sd_smallval")) log_medians_df_3sd_smallval else NULL,
  regression_models = if(exists("Model1Medians_3sd_smallval")) list(model1 = Model1Medians_3sd_smallval, model2 = Model2Medians_3sd_smallval, model3 = Model3Medians_3sd_smallval) else NULL,
  regression_summary = if(exists("regression_summary_medians_3sd_smallval")) regression_summary_medians_3sd_smallval else NULL,
  aic_values = if(exists("AIC1Medians_3sd_smallval")) c(AIC1 = AIC1Medians_3sd_smallval, AIC2 = AIC2Medians_3sd_smallval, AIC3 = AIC3Medians_3sd_smallval) else NULL
)
```

#### 4b. (Plus one to all values): Plots and Reporting (WITH 3SD Removal)

```{r}
# Check if models exist before plotting
if(exists("Model1Medians_3sd_plusone") && exists("dataforAICMedians_3sd_plusone_clean") && nrow(dataforAICMedians_3sd_plusone_clean) > 0) {

  # Average Median vs Reasonable Median
  plot1_median_3sd_plusone <- ggplot(dataforAICMedians_3sd_plusone_clean, aes(x = Average, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "blue") +
    labs(title = "Model 1 (WITH 3SD, Log+1): Median Average vs Reasonable",
         subtitle = paste("AIC =", round(AIC1Medians_3sd_plusone, 2), ", R² =", round(r2_model1_median_3sd_plusone, 3)),
         x = "Log (+1) Median Average Rating (3SD Removed)",
         y = "Log (+1) Median Reasonable Rating (3SD Removed)") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Ideal Median vs Reasonable Median
  plot2_median_3sd_plusone <- ggplot(dataforAICMedians_3sd_plusone_clean, aes(x = Ideal, y = Reasonable)) +
    geom_point(size = 3, alpha = 0.7) + geom_smooth(method = "lm", se = TRUE, color = "red") +
    labs(title = "Model 2 (WITH 3SD, Log+1): Median Ideal vs Reasonable",
         subtitle = paste("AIC =", round(AIC2Medians_3sd_plusone, 2), ", R² =", round(r2_model2_median_3sd_plusone, 3)),
         x = "Log (+1) Median Ideal Rating (3SD Removed)",
         y = "Log (+1) Median Reasonable Rating (3SD Removed)") +
    theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Average effect)
  new_data_median_3sd_plusone <- expand.grid( Average = seq(min(dataforAICMedians_3sd_plusone_clean$Average, na.rm=TRUE), max(dataforAICMedians_3sd_plusone_clean$Average, na.rm=TRUE), length.out = 100), Ideal = median(dataforAICMedians_3sd_plusone_clean$Ideal, na.rm=TRUE) )
  new_data_median_3sd_plusone <- new_data_median_3sd_plusone[is.finite(new_data_median_3sd_plusone$Average) & is.finite(new_data_median_3sd_plusone$Ideal),]
  if(nrow(new_data_median_3sd_plusone)>0){ new_data_median_3sd_plusone$predicted_reasonable <- predict(Model3Medians_3sd_plusone, newdata = new_data_median_3sd_plusone) } else { new_data_median_3sd_plusone <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric()) }
  plot3_median_3sd_plusone <- ggplot(dataforAICMedians_3sd_plusone_clean, aes(x = Average, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data_median_3sd_plusone, aes(y = predicted_reasonable), color = "blue", size = 1) + labs(title = "Model 3 (WITH 3SD, Log+1): Effect of Median Average", subtitle = paste("AIC =", round(AIC3Medians_3sd_plusone, 2), ", R² =", round(r2_model3_median_3sd_plusone, 3)), x = "Log (+1) Median Average Rating (3SD Removed)", y = "Log (+1) Median Reasonable Rating (3SD Removed)") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Model 3 (Ideal effect)
  new_data2_median_3sd_plusone <- expand.grid( Average = median(dataforAICMedians_3sd_plusone_clean$Average, na.rm=TRUE), Ideal = seq(min(dataforAICMedians_3sd_plusone_clean$Ideal, na.rm=TRUE), max(dataforAICMedians_3sd_plusone_clean$Ideal, na.rm=TRUE), length.out = 100) )
  new_data2_median_3sd_plusone <- new_data2_median_3sd_plusone[is.finite(new_data2_median_3sd_plusone$Average) & is.finite(new_data2_median_3sd_plusone$Ideal),]
  if(nrow(new_data2_median_3sd_plusone)>0){ new_data2_median_3sd_plusone$predicted_reasonable <- predict(Model3Medians_3sd_plusone, newdata = new_data2_median_3sd_plusone) } else { new_data2_median_3sd_plusone <- data.frame(Average=numeric(), Ideal=numeric(), predicted_reasonable=numeric()) }
  plot4_median_3sd_plusone <- ggplot(dataforAICMedians_3sd_plusone_clean, aes(x = Ideal, y = Reasonable)) + geom_point(size = 3, alpha = 0.5) + geom_line(data = new_data2_median_3sd_plusone, aes(y = predicted_reasonable), color = "red", size = 1) + labs(title = "Model 3 (WITH 3SD, Log+1): Effect of Median Ideal", subtitle = paste("AIC =", round(AIC3Medians_3sd_plusone, 2), ", R² =", round(r2_model3_median_3sd_plusone, 3)), x = "Log (+1) Median Ideal Rating (3SD Removed)", y = "Log (+1) Median Reasonable Rating (3SD Removed)") + theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9) )

  # Display plots
  print(plot1_median_3sd_plusone)
  print(plot2_median_3sd_plusone)
  print(plot3_median_3sd_plusone)
  print(plot4_median_3sd_plusone)

  # Save plots
  ggsave("model1_median_avg_reas_3sd_plusone.png", plot1_median_3sd_plusone, width = 8, height = 6, dpi = 300)
  ggsave("model2_median_ideal_reas_3sd_plusone.png", plot2_median_3sd_plusone, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_avg_eff_3sd_plusone.png", plot3_median_3sd_plusone, width = 8, height = 6, dpi = 300)
  ggsave("model3_median_ideal_eff_3sd_plusone.png", plot4_median_3sd_plusone, width = 8, height = 6, dpi = 300)
  grid_plots_median_3sd_plusone <- grid.arrange(plot1_median_3sd_plusone, plot2_median_3sd_plusone, plot3_median_3sd_plusone, plot4_median_3sd_plusone, ncol = 2)
  ggsave("all_median_plots_3sd_plusone.png", grid_plots_median_3sd_plusone, width = 14, height = 10, dpi = 300)

  # Correlation matrix
  cor_data_3sd_plusone <- dataforAICMedians_3sd_plusone_clean[complete.cases(dataforAICMedians_3sd_plusone_clean),]
  if(nrow(cor_data_3sd_plusone) > 1) {
   cor_matrix_3sd_plusone <- cor(cor_data_3sd_plusone, use = "complete.obs")
   corrplot(cor_matrix_3sd_plusone, method = "color", type = "upper", addCoef.col = "black", tl.col = "black", tl.srt = 45, diag = FALSE, title = "Correlation Matrix (WITH 3SD, Log Plus One)", mar = c(0,0,1,0))
  } else { cat("Not enough data for correlation matrix (WITH 3SD, Log Plus One).\n") }

  # Coefficient tables
  model1_coefs_3sd_plusone <- get_model_coefs(Model1Medians_3sd_plusone)
  model2_coefs_3sd_plusone <- get_model_coefs(Model2Medians_3sd_plusone)
  model3_coefs_3sd_plusone <- get_model_coefs(Model3Medians_3sd_plusone)
  model1_coefs_3sd_plusone$p_value <- sapply(model1_coefs_3sd_plusone$p_value, format_pvalue)
  model2_coefs_3sd_plusone$p_value <- sapply(model2_coefs_3sd_plusone$p_value, format_pvalue)
  model3_coefs_3sd_plusone$p_value <- sapply(model3_coefs_3sd_plusone$p_value, format_pvalue)
  kable(model1_coefs_3sd_plusone, caption = "Model 1 Coeffs (WITH 3SD, Log Plus One)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model2_coefs_3sd_plusone, caption = "Model 2 Coeffs (WITH 3SD, Log Plus One)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
  kable(model3_coefs_3sd_plusone, caption = "Model 3 Coeffs (WITH 3SD, Log Plus One)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

  # Print model summaries
  cat("\nModel Summaries (WITH 3SD, Log Plus One):\n")
  print(summary(Model1Medians_3sd_plusone))
  print(summary(Model2Medians_3sd_plusone))
  print(summary(Model3Medians_3sd_plusone))

} else {
  cat("Skipping plots and summaries for (WITH 3SD, Log Plus One) due to insufficient data.\n")
}

# Store results
analysis_3_results_3sd_plusone <- list(
  medians_by_question = if(exists("medians_df_3sd")) medians_df_3sd else NULL,
  log_medians_by_question = if(exists("log_medians_df_3sd_plusone")) log_medians_df_3sd_plusone else NULL,
  regression_models = if(exists("Model1Medians_3sd_plusone")) list(model1 = Model1Medians_3sd_plusone, model2 = Model2Medians_3sd_plusone, model3 = Model3Medians_3sd_plusone) else NULL,
  regression_summary = if(exists("regression_summary_medians_3sd_plusone")) regression_summary_medians_3sd_plusone else NULL,
  aic_values = if(exists("AIC1Medians_3sd_plusone")) c(AIC1 = AIC1Medians_3sd_plusone, AIC2 = AIC2Medians_3sd_plusone, AIC3 = AIC3Medians_3sd_plusone) else NULL
)
```

# Analysis 4 [NO 3 SD Outlier Removal]: Overall results, intermediacy with median ratings

Step 1 and Step 2 have been completed in the earlier analysis.

#### Functions for Analysis 4

```{r}
# Function to check if reasonable is on the "ideal side" of average
# Equal median ratings are treated as being on the predicted side
is_ideal_side_median <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
    return(NA)
  }
  # Check if distance to ideal is less than or equal to distance to average
  ifelse(abs(reasonable - ideal) <= abs(reasonable - average), 1, 0)
}

# Function to check if reasonable is on the "average side" of ideal
# Equal median ratings are treated as being on the predicted side
is_average_side_median <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
      return(NA)
  }
  # Check if distance to average is less than or equal to distance to ideal
  ifelse(abs(reasonable - average) <= abs(reasonable - ideal), 1, 0)
}

# Function to check if reasonable falls between average and ideal (inclusive/liberal)
# Handles cases where average == ideal
is_both_sides_median_liberal <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
      return(NA)
  }
  # Check if reasonable is numerically between average and ideal, inclusive
  # This works regardless of whether average > ideal or ideal > average
  ifelse((reasonable >= min(average, ideal)) & (reasonable <= max(average, ideal)), 1, 0)
}

# Function to check if reasonable falls between average and ideal (conservative)
# Handles cases where average is NOT == ideal
is_both_sides_median_conservative <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
    return(NA)
  }
  # Check if reasonable is numerically between average and ideal, conservative
  ifelse((reasonable > min(average, ideal)) & (reasonable < max(average, ideal)), 1, 0)
}
```

#### Steps 3, 4, 5: Intermediacy Calculations (NO 3SD Removal)

```{r}
# --- Calculate all vectors ---
ideal_side_vector_median_no3sd <- mapply(is_ideal_side_median, column_medians_average_no3sd, column_medians_ideal_no3sd, column_medians_reasonable_no3sd)
average_side_vector_median_no3sd <- mapply(is_average_side_median, column_medians_average_no3sd, column_medians_ideal_no3sd, column_medians_reasonable_no3sd)
both_sides_vector_median_no3sd_liberal <- mapply(is_both_sides_median_liberal, column_medians_average_no3sd, column_medians_ideal_no3sd, column_medians_reasonable_no3sd)
both_sides_vector_median_no3sd_conservative <- mapply(is_both_sides_median_conservative, column_medians_average_no3sd, column_medians_ideal_no3sd, column_medians_reasonable_no3sd)

# --- Calculate counts and valid Ns ---
count_ideal_side_median_no3sd <- sum(ideal_side_vector_median_no3sd, na.rm = TRUE)
valid_questions_ideal_no3sd <- sum(!is.na(ideal_side_vector_median_no3sd))
count_average_side_median_no3sd <- sum(average_side_vector_median_no3sd, na.rm = TRUE)
valid_questions_avg_no3sd <- sum(!is.na(average_side_vector_median_no3sd))
count_both_sides_median_no3sd_liberal <- sum(both_sides_vector_median_no3sd_liberal, na.rm = TRUE)
valid_questions_both_no3sd_liberal <- sum(!is.na(both_sides_vector_median_no3sd_liberal))
count_both_sides_median_no3sd_conservative <- sum(both_sides_vector_median_no3sd_conservative, na.rm = TRUE)
valid_questions_both_no3sd_conservative <- sum(!is.na(both_sides_vector_median_no3sd_conservative))

# --- Perform binomial tests ---
p_val_ideal_no3sd <- NA;
if (valid_questions_ideal_no3sd > 0) {
  binomial_result_ideal_median_no3sd <- binom.test(count_ideal_side_median_no3sd, valid_questions_ideal_no3sd, p = 0.5, alternative = "greater")
  p_val_ideal_no3sd <- binomial_result_ideal_median_no3sd$p.value
}

p_val_avg_no3sd <- NA;
if (valid_questions_avg_no3sd > 0) {
  binomial_result_avg_side_median_no3sd <- binom.test(count_average_side_median_no3sd, valid_questions_avg_no3sd, p = 0.5, alternative = "greater")
  p_val_avg_no3sd <- binomial_result_avg_side_median_no3sd$p.value
}

p_val_both_liberal_no3sd <- NA;
if (valid_questions_both_no3sd_liberal > 0) {
  binomial_result_both_sides_liberal_median_no3sd <- binom.test(count_both_sides_median_no3sd_liberal, valid_questions_both_no3sd_liberal, p = 1/3, alternative = "two.sided")
  p_val_both_liberal_no3sd <- binomial_result_both_sides_liberal_median_no3sd$p.value
}

p_val_both_conservative_no3sd <- NA;
if (valid_questions_both_no3sd_conservative > 0) {
  binomial_result_both_sides_conservative_median_no3sd <- binom.test(count_both_sides_median_no3sd_conservative, valid_questions_both_no3sd_conservative, p = 1/3, alternative = "two.sided")
  p_val_both_conservative_no3sd <- binomial_result_both_sides_conservative_median_no3sd$p.value
}

# --- Create ONE combined summary table ---
intermediacy_summary_no3sd <- data.frame(
  Test = c("On Ideal Side of Average", "On Average Side of Ideal", "Between (Liberal)", "Between (Conservative)"),
  Count = c(count_ideal_side_median_no3sd, count_average_side_median_no3sd, count_both_sides_median_no3sd_liberal, count_both_sides_median_no3sd_conservative),
  Total_Valid = c(valid_questions_ideal_no3sd, valid_questions_avg_no3sd, valid_questions_both_no3sd_liberal, valid_questions_both_no3sd_conservative),
  Expected_Prop = c(0.5, 0.5, 1/3, 1/3),
  p_value = c(p_val_ideal_no3sd, p_val_avg_no3sd, p_val_both_liberal_no3sd, p_val_both_conservative_no3sd)
)

# Format proportions and p-values
intermediacy_summary_no3sd$Proportion <- scales::percent(intermediacy_summary_no3sd$Count / intermediacy_summary_no3sd$Total_Valid, accuracy = 0.1)
intermediacy_summary_no3sd$Expected_Prop <- scales::percent(intermediacy_summary_no3sd$Expected_Prop, accuracy = 0.1)
intermediacy_summary_no3sd$p_value <- sapply(intermediacy_summary_no3sd$p_value, format_pvalue)

# Display the summary table
kable(intermediacy_summary_no3sd[,c("Test", "Count", "Total_Valid", "Proportion", "Expected_Prop", "p_value")],
      caption = "Intermediacy Binomial Tests (NO 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```
#### 6. Plots and Reporting (Intermediacy - Median Analysis, NO 3SD Removed)

```{r}
# Create a table showing the results for each question, including both intermediacy measures
question_position_summary_median_no3sd <- data.frame(
  Question = names(column_medians_average_no3sd),
  Average_Value = column_medians_average_no3sd,
  Ideal_Value = column_medians_ideal_no3sd,
  Reasonable_Value = column_medians_reasonable_no3sd,
  On_Ideal_Side = ideal_side_vector_median_no3sd,
  On_Average_Side = average_side_vector_median_no3sd,
  Between_Liberal = both_sides_vector_median_no3sd_liberal,
  Between_Conservative = both_sides_vector_median_no3sd_conservative
)

# Categorize for Liberal Analysis
question_position_summary_median_no3sd$Position_Liberal <- "Other/NA"
question_position_summary_median_no3sd$Position_Liberal[question_position_summary_median_no3sd$Between_Liberal == 1] <- "Between (Liberal)"
question_position_summary_median_no3sd$Position_Liberal[question_position_summary_median_no3sd$Between_Liberal == 0 & question_position_summary_median_no3sd$On_Ideal_Side == 1 & question_position_summary_median_no3sd$On_Average_Side == 0] <- "Beyond Ideal"
question_position_summary_median_no3sd$Position_Liberal[question_position_summary_median_no3sd$Between_Liberal == 0 & question_position_summary_median_no3sd$On_Average_Side == 1 & question_position_summary_median_no3sd$On_Ideal_Side == 0] <- "Beyond Average"
question_position_summary_median_no3sd$Position_Liberal[
    !is.na(question_position_summary_median_no3sd$Average_Value) &
    !is.na(question_position_summary_median_no3sd$Ideal_Value) &
    question_position_summary_median_no3sd$Average_Value == question_position_summary_median_no3sd$Ideal_Value] <- "Average = Ideal"

# Categorize for Conservative Analysis
question_position_summary_median_no3sd$Position_Conservative <- "Other/NA"
question_position_summary_median_no3sd$Position_Conservative[question_position_summary_median_no3sd$Between_Conservative == 1] <- "Between (Conservative)"
question_position_summary_median_no3sd$Position_Conservative[question_position_summary_median_no3sd$Between_Conservative == 0 & question_position_summary_median_no3sd$On_Ideal_Side == 1 & question_position_summary_median_no3sd$On_Average_Side == 0] <- "Beyond Ideal"
question_position_summary_median_no3sd$Position_Conservative[question_position_summary_median_no3sd$Between_Conservative == 0 & question_position_summary_median_no3sd$On_Average_Side == 1 & question_position_summary_median_no3sd$On_Ideal_Side == 0] <- "Beyond Average"
question_position_summary_median_no3sd$Position_Conservative[
    !is.na(question_position_summary_median_no3sd$Average_Value) &
    !is.na(question_position_summary_median_no3sd$Ideal_Value) &
    question_position_summary_median_no3sd$Average_Value == question_position_summary_median_no3sd$Ideal_Value] <- "Average = Ideal"


# Display the question position summary table
kable(question_position_summary_median_no3sd[, c("Question", "Average_Value", "Ideal_Value", "Reasonable_Value", "Position_Liberal", "Position_Conservative")],
      caption = "Position of Median Reasonable Rating (NO 3SD Removal) Relative to Average and Ideal") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

# --- Liberal Distribution ---
position_counts_liberal_no3sd <- as.data.frame(table(question_position_summary_median_no3sd$Position_Liberal))
names(position_counts_liberal_no3sd) <- c("Position", "Count")
kable(position_counts_liberal_no3sd, caption = "Distribution of Position Categories (Liberal, NO 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

position_distribution_plot_liberal_no3sd <- ggplot(position_counts_liberal_no3sd, aes(x = Position, y = Count, fill = Position)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(Count)), vjust = -0.5, size = 4) +
  labs(title = "Distribution of Position Categories (Liberal, NO 3SD Removal)",
       subtitle = "Where 'Reasonable' falls relative to 'Average' and 'Ideal' (inclusive)",
       x = "Position Category", y = "Number of Questions") +
  theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 15, hjust = 1), legend.position = "none")
print(position_distribution_plot_liberal_no3sd)
ggsave("position_distribution_median_liberal_no3sd.png", position_distribution_plot_liberal_no3sd, width = 10, height = 7, dpi = 300)


# --- Conservative Distribution ---
position_counts_conservative_no3sd <- as.data.frame(table(question_position_summary_median_no3sd$Position_Conservative))
names(position_counts_conservative_no3sd) <- c("Position", "Count")
kable(position_counts_conservative_no3sd, caption = "Distribution of Position Categories (Conservative, NO 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

position_distribution_plot_conservative_no3sd <- ggplot(position_counts_conservative_no3sd, aes(x = Position, y = Count, fill = Position)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(Count)), vjust = -0.5, size = 4) +
  labs(title = "Distribution of Position Categories (Conservative, NO 3SD Removal)",
       subtitle = "Where 'Reasonable' falls relative to 'Average' and 'Ideal' (exclusive)",
       x = "Position Category", y = "Number of Questions") +
  theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 15, hjust = 1), legend.position = "none")
print(position_distribution_plot_conservative_no3sd)
ggsave("position_distribution_median_conservative_no3sd.png", position_distribution_plot_conservative_no3sd, width = 10, height = 7, dpi = 300)

# --- Liberal Scatterplot ---
plot_data_intermediacy_no3sd <- question_position_summary_median_no3sd %>% filter(!is.na(Average_Value) & !is.na(Ideal_Value) & !is.na(Reasonable_Value))
prop_both_liberal_fmt <- scales::percent(ifelse(valid_questions_both_no3sd_liberal > 0, count_both_sides_median_no3sd_liberal/valid_questions_both_no3sd_liberal, 0), accuracy=0.1)

intermediacy_plot_liberal_no3sd <- ggplot(plot_data_intermediacy_no3sd, aes(x = Average_Value, y = Ideal_Value)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
  geom_point(color = "gray60", size = 3, alpha = 0.6) +
  geom_point(aes(x = Average_Value, y = Reasonable_Value, color = Position_Liberal), size = 4) +
  geom_segment(aes(x = Average_Value, xend = Average_Value, y = Ideal_Value, yend = Reasonable_Value, color = Position_Liberal), linetype = "dotted", size = 0.5, alpha = 0.7) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Intermediacy Analysis (Liberal, NO 3SD Removal): Position of Reasonable",
       subtitle = paste0("Between Avg and Ideal: ", count_both_sides_median_no3sd_liberal, " of ", valid_questions_both_no3sd_liberal, " (", prop_both_liberal_fmt, ")"),
       x = "Median Average Rating (NO 3SD Removal)", y = "Median Rating Value (NO 3SD Removal)", color = "Position Category (Liberal)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9), legend.position = "bottom")
print(intermediacy_plot_liberal_no3sd)
ggsave("intermediacy_analysis_median_liberal_no3sd.png", intermediacy_plot_liberal_no3sd, width = 10, height = 8, dpi = 300)


# --- Conservative Scatterplot ---
prop_both_conservative_fmt <- scales::percent(ifelse(valid_questions_both_no3sd_conservative > 0, count_both_sides_median_no3sd_conservative/valid_questions_both_no3sd_conservative, 0), accuracy=0.1)

intermediacy_plot_conservative_no3sd <- ggplot(plot_data_intermediacy_no3sd, aes(x = Average_Value, y = Ideal_Value)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
  geom_point(color = "gray60", size = 3, alpha = 0.6) +
  geom_point(aes(x = Average_Value, y = Reasonable_Value, color = Position_Conservative), size = 4) +
  geom_segment(aes(x = Average_Value, xend = Average_Value, y = Ideal_Value, yend = Reasonable_Value, color = Position_Conservative), linetype = "dotted", size = 0.5, alpha = 0.7) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Intermediacy Analysis (Conservative, NO 3SD Removal): Position of Reasonable",
       subtitle = paste0("Between Avg and Ideal: ", count_both_sides_median_no3sd_conservative, " of ", valid_questions_both_no3sd_conservative, " (", prop_both_conservative_fmt, ")"),
       x = "Median Average Rating (NO 3SD Removal)", y = "Median Rating Value (NO 3SD Removal)", color = "Position Category (Conservative)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9), legend.position = "bottom")
print(intermediacy_plot_conservative_no3sd)
ggsave("intermediacy_analysis_median_conservative_no3sd.png", intermediacy_plot_conservative_no3sd, width = 10, height = 8, dpi = 300)

# --- Liberal Rating Patterns Plot ---
ratings_long_liberal_no3sd <- question_position_summary_median_no3sd %>%
  select(Question, Average_Value, Ideal_Value, Reasonable_Value, Position_Liberal) %>%
  pivot_longer(cols = c(Average_Value, Ideal_Value, Reasonable_Value), names_to = "Rating_Type", values_to = "Value") %>%
  mutate(Rating_Type = factor(gsub("_Value", "", Rating_Type), levels = c("Average", "Reasonable", "Ideal"))) %>%
  filter(!is.na(Value))

rating_patterns_plot_liberal_no3sd <- ggplot(ratings_long_liberal_no3sd, aes(x = Rating_Type, y = Value, group = Question, color = Position_Liberal)) +
  geom_line(alpha = 0.5) + geom_point(size = 2.5, alpha=0.7) + facet_wrap(~ Position_Liberal, scales = "free_y") +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Rating Patterns by Position Category (Liberal, NO 3SD Removal)",
       subtitle = "How Average, Ideal, and Reasonable median ratings relate within each category",
       x = "Rating Type", y = "Median Value (NO 3SD Removal)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), strip.text = element_text(size=10, face="bold"), legend.position = "none")
print(rating_patterns_plot_liberal_no3sd)
ggsave("rating_patterns_by_position_liberal_no3sd.png", rating_patterns_plot_liberal_no3sd, width = 12, height = 8, dpi = 300)


# --- Conservative Rating Patterns Plot ---
ratings_long_conservative_no3sd <- question_position_summary_median_no3sd %>%
  select(Question, Average_Value, Ideal_Value, Reasonable_Value, Position_Conservative) %>%
  pivot_longer(cols = c(Average_Value, Ideal_Value, Reasonable_Value), names_to = "Rating_Type", values_to = "Value") %>%
  mutate(Rating_Type = factor(gsub("_Value", "", Rating_Type), levels = c("Average", "Reasonable", "Ideal"))) %>%
  filter(!is.na(Value))

rating_patterns_plot_conservative_no3sd <- ggplot(ratings_long_conservative_no3sd, aes(x = Rating_Type, y = Value, group = Question, color = Position_Conservative)) +
  geom_line(alpha = 0.5) + geom_point(size = 2.5, alpha=0.7) + facet_wrap(~ Position_Conservative, scales = "free_y") +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Rating Patterns by Position Category (Conservative, NO 3SD Removal)",
       subtitle = "How Average, Ideal, and Reasonable median ratings relate within each category",
       x = "Rating Type", y = "Median Value (NO 3SD Removal)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), strip.text = element_text(size=10, face="bold"), legend.position = "none")
print(rating_patterns_plot_conservative_no3sd)
ggsave("rating_patterns_by_position_conservative_no3sd.png", rating_patterns_plot_conservative_no3sd, width = 12, height = 8, dpi = 300)

# Store results for this entire analysis chunk
analysis_4_results_no3sd <- list(
  ideal_side = list(vector=ideal_side_vector_median_no3sd, count=count_ideal_side_median_no3sd, valid_n=valid_questions_ideal_no3sd, binomial_test=binomial_result_ideal_median_no3sd),
  average_side = list(vector=average_side_vector_median_no3sd, count=count_average_side_median_no3sd, valid_n=valid_questions_avg_no3sd, binomial_test=binomial_result_avg_side_median_no3sd),
  both_sides_liberal = list(vector=both_sides_vector_median_no3sd_liberal, count=count_both_sides_median_no3sd_liberal, valid_n=valid_questions_both_no3sd_liberal, binomial_test=binomial_result_both_sides_liberal_median_no3sd),
  both_sides_conservative = list(vector=both_sides_vector_median_no3sd_conservative, count=count_both_sides_median_no3sd_conservative, valid_n=valid_questions_both_no3sd_conservative, binomial_test=binomial_result_both_sides_conservative_median_no3sd),
  combined_summary = intermediacy_summary_no3sd,
  question_position_summary = question_position_summary_median_no3sd
)
```

# Analysis 4 [WITH 3 SD Outlier Removal]: Overall results, intermediacy with median ratings

Step 1 and Step 2 have been completed in the earlier analysis.

#### Functions for Analysis 4

```{r}
# Function to check if reasonable is on the "ideal side" of average
# Equal median ratings are treated as being on the predicted side
is_ideal_side_median <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
    return(NA)
  }
  # Check if distance to ideal is less than or equal to distance to average
  ifelse(abs(reasonable - ideal) <= abs(reasonable - average), 1, 0)
}

# Function to check if reasonable is on the "average side" of ideal
# Equal median ratings are treated as being on the predicted side
is_average_side_median <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
      return(NA)
  }
  # Check if distance to average is less than or equal to distance to ideal
  ifelse(abs(reasonable - average) <= abs(reasonable - ideal), 1, 0)
}

# Function to check if reasonable falls between average and ideal (inclusive/liberal)
# Handles cases where average == ideal
is_both_sides_median_liberal <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
      return(NA)
  }
  # Check if reasonable is numerically between average and ideal, inclusive
  # This works regardless of whether average > ideal or ideal > average
  ifelse((reasonable >= min(average, ideal)) & (reasonable <= max(average, ideal)), 1, 0)
}

# Function to check if reasonable falls between average and ideal (conservative)
# Handles cases where average is NOT == ideal
is_both_sides_median_conservative <- function(average, ideal, reasonable) {
  if (any(is.na(c(average, ideal, reasonable)))) {
    return(NA)
  }
  # Check if reasonable is numerically between average and ideal, conservative
  ifelse((reasonable > min(average, ideal)) & (reasonable < max(average, ideal)), 1, 0)
}
```

#### Steps 3, 4, 5: Intermediacy Calculations (WITH 3SD Removal)

```{r}
# --- Calculate all vectors ---
column_medians_average_3sd <- sapply(Data_All_Average_Filtered[, question_cols], median, na.rm = TRUE)
column_medians_ideal_3sd <- sapply(Data_All_Ideal_Filtered[, question_cols], median, na.rm = TRUE)
column_medians_reasonable_3sd <- sapply(Data_All_Reasonable_Filtered[, question_cols], median, na.rm = TRUE)

ideal_side_vector_median_3sd <- mapply(is_ideal_side_median, column_medians_average_3sd, column_medians_ideal_3sd, column_medians_reasonable_3sd)
average_side_vector_median_3sd <- mapply(is_average_side_median, column_medians_average_3sd, column_medians_ideal_3sd, column_medians_reasonable_3sd)
both_sides_vector_median_3sd_liberal <- mapply(is_both_sides_median_liberal, column_medians_average_3sd, column_medians_ideal_3sd, column_medians_reasonable_3sd)
both_sides_vector_median_3sd_conservative <- mapply(is_both_sides_median_conservative, column_medians_average_3sd, column_medians_ideal_3sd, column_medians_reasonable_3sd)

# --- Calculate counts and valid Ns ---
count_ideal_side_median_3sd <- sum(ideal_side_vector_median_3sd, na.rm = TRUE)
valid_questions_ideal_3sd <- sum(!is.na(ideal_side_vector_median_3sd))
count_average_side_median_3sd <- sum(average_side_vector_median_3sd, na.rm = TRUE)
valid_questions_avg_3sd <- sum(!is.na(average_side_vector_median_3sd))
count_both_sides_median_3sd_liberal <- sum(both_sides_vector_median_3sd_liberal, na.rm = TRUE)
valid_questions_both_3sd_liberal <- sum(!is.na(both_sides_vector_median_3sd_liberal))
count_both_sides_median_3sd_conservative <- sum(both_sides_vector_median_3sd_conservative, na.rm = TRUE)
valid_questions_both_3sd_conservative <- sum(!is.na(both_sides_vector_median_3sd_conservative))


# --- Perform binomial tests ---
p_val_ideal_3sd <- NA;
if (valid_questions_ideal_3sd > 0) {
  binomial_result_ideal_median_3sd <- binom.test(count_ideal_side_median_3sd, valid_questions_ideal_3sd, p = 0.5, alternative = "greater")
  p_val_ideal_3sd <- binomial_result_ideal_median_3sd$p.value
}

p_val_avg_3sd <- NA;
if (valid_questions_avg_3sd > 0) {
  binomial_result_avg_side_median_3sd <- binom.test(count_average_side_median_3sd, valid_questions_avg_3sd, p = 0.5, alternative = "greater")
  p_val_avg_3sd <- binomial_result_avg_side_median_3sd$p.value
}

p_val_both_liberal_3sd <- NA;
if (valid_questions_both_3sd_liberal > 0) {
  binomial_result_both_sides_liberal_median_3sd <- binom.test(count_both_sides_median_3sd_liberal, valid_questions_both_3sd_liberal, p = 1/3, alternative = "two.sided")
  p_val_both_liberal_3sd <- binomial_result_both_sides_liberal_median_3sd$p.value
}

p_val_both_conservative_3sd <- NA;
if (valid_questions_both_3sd_conservative > 0) {
  binomial_result_both_sides_conservative_median_3sd <- binom.test(count_both_sides_median_3sd_conservative, valid_questions_both_3sd_conservative, p = 1/3, alternative = "two.sided")
  p_val_both_conservative_3sd <- binomial_result_both_sides_conservative_median_3sd$p.value
}

# --- Create ONE combined summary table for all tests ---
intermediacy_summary_3sd <- data.frame(
  Test = c("On Ideal Side of Average", "On Average Side of Ideal", "Between (Liberal)", "Between (Conservative)"),
  Count = c(count_ideal_side_median_3sd, count_average_side_median_3sd, count_both_sides_median_3sd_liberal, count_both_sides_median_3sd_conservative),
  Total_Valid = c(valid_questions_ideal_3sd, valid_questions_avg_3sd, valid_questions_both_3sd_liberal, valid_questions_both_3sd_conservative),
  Expected_Prop = c(0.5, 0.5, 1/3, 1/3),
  p_value = c(p_val_ideal_3sd, p_val_avg_3sd, p_val_both_liberal_3sd, p_val_both_conservative_3sd)
)

# Calculate and format proportions
intermediacy_summary_3sd$Proportion <- scales::percent(intermediacy_summary_3sd$Count / intermediacy_summary_3sd$Total_Valid, accuracy = 0.1)
intermediacy_summary_3sd$Expected_Prop <- scales::percent(intermediacy_summary_3sd$Expected_Prop, accuracy = 0.1)
intermediacy_summary_3sd$p_value <- sapply(intermediacy_summary_3sd$p_value, format_pvalue)


# Display the summary table
kable(intermediacy_summary_3sd[,c("Test", "Count", "Total_Valid", "Proportion", "Expected_Prop", "p_value")],
      caption = "Intermediacy Binomial Tests (WITH 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```

#### 6. Plots and Reporting (Intermediacy - Median Analysis, WITH 3SD Removed)

```{r}
# Create a table showing the results for each question, including columns for both liberal and conservative intermediacy
question_position_summary_median_3sd <- data.frame(
  Question = names(column_medians_average_3sd),
  Average_Value = column_medians_average_3sd,
  Ideal_Value = column_medians_ideal_3sd,
  Reasonable_Value = column_medians_reasonable_3sd,
  On_Ideal_Side = ideal_side_vector_median_3sd,
  On_Average_Side = average_side_vector_median_3sd,
  Between_Liberal = both_sides_vector_median_3sd_liberal,
  Between_Conservative = both_sides_vector_median_3sd_conservative
)

# Categorize for Liberal Analysis
question_position_summary_median_3sd$Position_Liberal <- "Other/NA"
question_position_summary_median_3sd$Position_Liberal[question_position_summary_median_3sd$Between_Liberal == 1] <- "Between (Liberal)"
question_position_summary_median_3sd$Position_Liberal[question_position_summary_median_3sd$Between_Liberal == 0 & question_position_summary_median_3sd$On_Ideal_Side == 1 & question_position_summary_median_3sd$On_Average_Side == 0] <- "Beyond Ideal"
question_position_summary_median_3sd$Position_Liberal[question_position_summary_median_3sd$Between_Liberal == 0 & question_position_summary_median_3sd$On_Average_Side == 1 & question_position_summary_median_3sd$On_Ideal_Side == 0] <- "Beyond Average"
question_position_summary_median_3sd$Position_Liberal[
    !is.na(question_position_summary_median_3sd$Average_Value) &
    !is.na(question_position_summary_median_3sd$Ideal_Value) &
    question_position_summary_median_3sd$Average_Value == question_position_summary_median_3sd$Ideal_Value] <- "Average = Ideal"

# Categorize for Conservative Analysis
question_position_summary_median_3sd$Position_Conservative <- "Other/NA"
question_position_summary_median_3sd$Position_Conservative[question_position_summary_median_3sd$Between_Conservative == 1] <- "Between (Conservative)"
question_position_summary_median_3sd$Position_Conservative[question_position_summary_median_3sd$Between_Conservative == 0 & question_position_summary_median_3sd$On_Ideal_Side == 1 & question_position_summary_median_3sd$On_Average_Side == 0] <- "Beyond Ideal"
question_position_summary_median_3sd$Position_Conservative[question_position_summary_median_3sd$Between_Conservative == 0 & question_position_summary_median_3sd$On_Average_Side == 1 & question_position_summary_median_3sd$On_Ideal_Side == 0] <- "Beyond Average"
question_position_summary_median_3sd$Position_Conservative[
    !is.na(question_position_summary_median_3sd$Average_Value) &
    !is.na(question_position_summary_median_3sd$Ideal_Value) &
    question_position_summary_median_3sd$Average_Value == question_position_summary_median_3sd$Ideal_Value] <- "Average = Ideal"


# Display the question position summary table
kable(question_position_summary_median_3sd[, c("Question", "Average_Value", "Ideal_Value", "Reasonable_Value", "Position_Liberal", "Position_Conservative")],
      caption = "Position of Median Reasonable Rating (WITH 3SD Removal) Relative to Average and Ideal") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

# --- Liberal Distribution ---
position_counts_liberal_3sd <- as.data.frame(table(question_position_summary_median_3sd$Position_Liberal))
names(position_counts_liberal_3sd) <- c("Position", "Count")
kable(position_counts_liberal_3sd, caption = "Distribution of Position Categories (Liberal, WITH 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

position_distribution_plot_liberal_3sd <- ggplot(position_counts_liberal_3sd, aes(x = Position, y = Count, fill = Position)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(Count)), vjust = -0.5, size = 4) +
  labs(title = "Distribution of Position Categories (Liberal, WITH 3SD Removal)",
       subtitle = "Where 'Reasonable' falls relative to 'Average' and 'Ideal' (inclusive)",
       x = "Position Category", y = "Number of Questions") +
  theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 15, hjust = 1), legend.position = "none")
print(position_distribution_plot_liberal_3sd)
ggsave("position_distribution_median_liberal_3sd_removed.png", position_distribution_plot_liberal_3sd, width = 10, height = 7, dpi = 300)


# --- Conservative Distribution ---
position_counts_conservative_3sd <- as.data.frame(table(question_position_summary_median_3sd$Position_Conservative))
names(position_counts_conservative_3sd) <- c("Position", "Count")
kable(position_counts_conservative_3sd, caption = "Distribution of Position Categories (Conservative, WITH 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

position_distribution_plot_conservative_3sd <- ggplot(position_counts_conservative_3sd, aes(x = Position, y = Count, fill = Position)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = paste0(Count)), vjust = -0.5, size = 4) +
  labs(title = "Distribution of Position Categories (Conservative, WITH 3SD Removal)",
       subtitle = "Where 'Reasonable' falls relative to 'Average' and 'Ideal' (exclusive)",
       x = "Position Category", y = "Number of Questions") +
  theme_minimal() + theme( plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 15, hjust = 1), legend.position = "none")
print(position_distribution_plot_conservative_3sd)
ggsave("position_distribution_median_conservative_3sd_removed.png", position_distribution_plot_conservative_3sd, width = 10, height = 7, dpi = 300)

# --- Liberal Scatterplot ---
plot_data_intermediacy_3sd <- question_position_summary_median_3sd %>% filter(!is.na(Average_Value) & !is.na(Ideal_Value) & !is.na(Reasonable_Value))
prop_both_liberal_3sd_fmt <- scales::percent(ifelse(valid_questions_both_3sd_liberal > 0, count_both_sides_median_3sd_liberal/valid_questions_both_3sd_liberal, 0), accuracy=0.1)

intermediacy_plot_liberal_3sd <- ggplot(plot_data_intermediacy_3sd, aes(x = Average_Value, y = Ideal_Value)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
  geom_point(color = "gray60", size = 3, alpha = 0.6) +
  geom_point(aes(x = Average_Value, y = Reasonable_Value, color = Position_Liberal), size = 4) +
  geom_segment(aes(x = Average_Value, xend = Average_Value, y = Ideal_Value, yend = Reasonable_Value, color = Position_Liberal), linetype = "dotted", size = 0.5, alpha = 0.7) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Intermediacy Analysis (Liberal, WITH 3SD Removal): Position of Reasonable",
       subtitle = paste0("Between Avg and Ideal: ", count_both_sides_median_3sd_liberal, " of ", valid_questions_both_3sd_liberal, " (", prop_both_liberal_3sd_fmt, ")"),
       x = "Median Average Rating (WITH 3SD Removal)", y = "Median Rating Value (WITH 3SD Removal)", color = "Position Category (Liberal)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9), legend.position = "bottom")
print(intermediacy_plot_liberal_3sd)
ggsave("intermediacy_analysis_median_liberal_3sd_removed.png", intermediacy_plot_liberal_3sd, width = 10, height = 8, dpi = 300)


# --- Conservative Scatterplot ---
prop_both_conservative_3sd_fmt <- scales::percent(ifelse(valid_questions_both_3sd_conservative > 0, count_both_sides_median_3sd_conservative/valid_questions_both_3sd_conservative, 0), accuracy=0.1)

intermediacy_plot_conservative_3sd <- ggplot(plot_data_intermediacy_3sd, aes(x = Average_Value, y = Ideal_Value)) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", alpha = 0.5) +
  geom_point(color = "gray60", size = 3, alpha = 0.6) +
  geom_point(aes(x = Average_Value, y = Reasonable_Value, color = Position_Conservative), size = 4) +
  geom_segment(aes(x = Average_Value, xend = Average_Value, y = Ideal_Value, yend = Reasonable_Value, color = Position_Conservative), linetype = "dotted", size = 0.5, alpha = 0.7) +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Intermediacy Analysis (Conservative, WITH 3SD Removal): Position of Reasonable",
       subtitle = paste0("Between Avg and Ideal: ", count_both_sides_median_3sd_conservative, " of ", valid_questions_both_3sd_conservative, " (", prop_both_conservative_3sd_fmt, ")"),
       x = "Median Average Rating (WITH 3SD Removal)", y = "Median Rating Value (WITH 3SD Removal)", color = "Position Category (Conservative)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text = element_text(size = 9), legend.position = "bottom")
print(intermediacy_plot_conservative_3sd)
ggsave("intermediacy_analysis_median_conservative_3sd_removed.png", intermediacy_plot_conservative_3sd, width = 10, height = 8, dpi = 300)

# --- Liberal Rating Patterns Plot ---
ratings_long_liberal_3sd <- question_position_summary_median_3sd %>%
  select(Question, Average_Value, Ideal_Value, Reasonable_Value, Position_Liberal) %>%
  pivot_longer(cols = c(Average_Value, Ideal_Value, Reasonable_Value), names_to = "Rating_Type", values_to = "Value") %>%
  mutate(Rating_Type = factor(gsub("_Value", "", Rating_Type), levels = c("Average", "Reasonable", "Ideal"))) %>%
  filter(!is.na(Value))

rating_patterns_plot_liberal_3sd <- ggplot(ratings_long_liberal_3sd, aes(x = Rating_Type, y = Value, group = Question, color = Position_Liberal)) +
  geom_line(alpha = 0.5) + geom_point(size = 2.5, alpha=0.7) + facet_wrap(~ Position_Liberal, scales = "free_y") +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Rating Patterns by Position Category (Liberal, WITH 3SD Removal)",
       subtitle = "How Average, Ideal, and Reasonable median ratings relate within each category",
       x = "Rating Type", y = "Median Value (WITH 3SD Removal)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), strip.text = element_text(size=10, face="bold"), legend.position = "none")
print(rating_patterns_plot_liberal_3sd)
ggsave("rating_patterns_by_position_liberal_3sd_removed.png", rating_patterns_plot_liberal_3sd, width = 12, height = 8, dpi = 300)


# --- Conservative Rating Patterns Plot ---
ratings_long_conservative_3sd <- question_position_summary_median_3sd %>%
  select(Question, Average_Value, Ideal_Value, Reasonable_Value, Position_Conservative) %>%
  pivot_longer(cols = c(Average_Value, Ideal_Value, Reasonable_Value), names_to = "Rating_Type", values_to = "Value") %>%
  mutate(Rating_Type = factor(gsub("_Value", "", Rating_Type), levels = c("Average", "Reasonable", "Ideal"))) %>%
  filter(!is.na(Value))

rating_patterns_plot_conservative_3sd <- ggplot(ratings_long_conservative_3sd, aes(x = Rating_Type, y = Value, group = Question, color = Position_Conservative)) +
  geom_line(alpha = 0.5) + geom_point(size = 2.5, alpha=0.7) + facet_wrap(~ Position_Conservative, scales = "free_y") +
  scale_color_brewer(palette = "Set1") +
  labs(title = "Rating Patterns by Position Category (Conservative, WITH 3SD Removal)",
       subtitle = "How Average, Ideal, and Reasonable median ratings relate within each category",
       x = "Rating Type", y = "Median Value (WITH 3SD Removal)") +
  theme_minimal() + theme(plot.title = element_text(size = 12, face = "bold"), plot.subtitle = element_text(size = 11), axis.title = element_text(size = 10), axis.text.x = element_text(size = 9, angle = 45, hjust = 1), axis.text.y = element_text(size = 9), strip.text = element_text(size=10, face="bold"), legend.position = "none")
print(rating_patterns_plot_conservative_3sd)
ggsave("rating_patterns_by_position_conservative_3sd_removed.png", rating_patterns_plot_conservative_3sd, width = 12, height = 8, dpi = 300)

# Store results for this entire analysis chunk
analysis_4_results_3sd <- list(
  ideal_side = list(vector=ideal_side_vector_median_3sd, count=count_ideal_side_median_3sd, valid_n=valid_questions_ideal_3sd, binomial_test=binomial_result_ideal_median_3sd),
  average_side = list(vector=average_side_vector_median_3sd, count=count_average_side_median_3sd, valid_n=valid_questions_avg_3sd, binomial_test=binomial_result_avg_side_median_3sd),
  both_sides_liberal = list(vector=both_sides_vector_median_3sd_liberal, count=count_both_sides_median_3sd_liberal, valid_n=valid_questions_both_3sd_liberal, binomial_test=binomial_result_both_sides_liberal_median_3sd),
  both_sides_conservative = list(vector=both_sides_vector_median_3sd_conservative, count=count_both_sides_median_3sd_conservative, valid_n=valid_questions_both_3sd_conservative, binomial_test=binomial_result_both_sides_conservative_median_3sd),
  combined_summary = intermediacy_summary_3sd,
  question_position_summary = question_position_summary_median_3sd
)
```

# Analysis 7 [NO 3 SD Removed]

```{r}
# Get unique country names
countries <- unique(Data_All$Country_name)
print(countries)
```

#### 7a (Small constant inf values): Country Regressions (NO 3SD Removal)

```{r}
# Create storage
country_results_median_no3sd_smallval <- list()

# Function to analyze median data for a single country (NO 3SD, Small Constant Log)
analyze_country_median_no3sd_smallval <- function(country, data_avg, data_ideal, data_reas, q_cols) {
  cat("\n========== Analyzing Median Data (NO 3SD, Log Small Const) for:", country, "==========\n")

  # Filter data by country AND apply attention check (using _Pass1 data)
  country_average_pass <- data_avg %>% filter(Country_name == country, q19 == 15)
  country_ideal_pass <- data_ideal %>% filter(Country_name == country, q19 == 15)
  country_reasonable_pass <- data_reas %>% filter(Country_name == country, q19 == 15)

  n_avg <- nrow(country_average_pass)
  n_ideal <- nrow(country_ideal_pass)
  n_reas <- nrow(country_reasonable_pass)

  cat("Participants after attention check:", n_avg, n_ideal, n_reas, "\n")

  if(n_avg < 1 || n_ideal < 1 || n_reas < 1) {
      cat("Insufficient participants for", country, "\n"); return(NULL)
  }

   convert_to_numeric <- function(df, cols) { df %>% mutate(across(all_of(cols), ~ suppressWarnings(as.numeric(as.character(.))))) }
   country_average_pass <- convert_to_numeric(country_average_pass, q_cols)
   country_ideal_pass <- convert_to_numeric(country_ideal_pass, q_cols)
   country_reasonable_pass <- convert_to_numeric(country_reasonable_pass, q_cols)

  # Calculate medians
  medians_avg <- if(n_avg > 0) sapply(country_average_pass[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_ideal <- if(n_ideal > 0) sapply(country_ideal_pass[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_reas <- if(n_reas > 0) sapply(country_reasonable_pass[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  names(medians_avg) <- q_cols; names(medians_ideal) <- q_cols; names(medians_reas) <- q_cols

  # Convert to log scale (Small Constant)
  log_medians_avg <- log_smallvalue(medians_avg)
  log_medians_ideal <- log_smallvalue(medians_ideal)
  log_medians_reas <- log_smallvalue(medians_reas)

  # Data frame for regression
  data_for_aic <- data.frame(Reasonable = log_medians_reas, Average = log_medians_avg, Ideal = log_medians_ideal)
  data_for_aic_clean <- data_for_aic %>% filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

  # Check for sufficient data points for regression
  if(nrow(data_for_aic_clean) < 5) {
    cat("Too few valid data points for regression analysis in", country, "\n")
    return(list(country=country, sample_sizes=list(after_attention=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_summary=NULL, best_model="Insufficient Data"))
  }

  # Run Regressions
  model1 <- lm(Reasonable ~ Average, data = data_for_aic_clean)
  aic1 <- AIC(model1); r2_1 <- summary(model1)$r.squared
  model2 <- lm(Reasonable ~ Ideal, data = data_for_aic_clean)
  aic2 <- AIC(model2); r2_2 <- summary(model2)$r.squared
  model3 <- lm(Reasonable ~ Average + Ideal, data = data_for_aic_clean)
  aic3 <- AIC(model3); r2_3 <- summary(model3)$r.squared

  # Regression summary
  reg_summary <- data.frame(Model=c("Avg", "Ideal", "Both"), AIC=c(aic1, aic2, aic3), R_squared=c(r2_1, r2_2, r2_3))
  best_model_idx <- which.min(c(aic1, aic2, aic3))
  best_model_name <- c("Average", "Ideal", "Hybrid")[best_model_idx]

  cat("Best model (NO 3SD, Log Small Const):", best_model_name, "\n")

  return(list(country=country, sample_sizes=list(after_attention=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_models=list(model1=model1, model2=model2, model3=model3), regression_summary=reg_summary, aic_values=c(Model1=aic1, Model2=aic2, Model3=aic3), best_model=best_model_name))
}

# Run analysis for each country
for(country in countries) {
  country_results_median_no3sd_smallval[[country]] <- analyze_country_median_no3sd_smallval(country, Data_All_Average_Pass1, Data_All_Ideal_Pass1, Data_All_Reasonable_Pass1, question_cols)
}

# Extract AIC summary
country_aic_summary_median_no3sd_smallval <- data.frame( Country = character(), AIC_Average = numeric(), AIC_Ideal = numeric(), AIC_Hybrid = numeric(), R2_Average = numeric(), R2_Ideal = numeric(), R2_Hybrid = numeric(), Best_Model = character(), N_Avg = integer(), N_Ideal = integer(), N_Reas = integer(), stringsAsFactors = FALSE )
for(country in countries) {
  res <- country_results_median_no3sd_smallval[[country]]
  if(!is.null(res)) {
      country_aic_summary_median_no3sd_smallval <- rbind(country_aic_summary_median_no3sd_smallval, data.frame( Country = country, AIC_Average = ifelse(!is.null(res$aic_values), res$aic_values["Model1"], NA), AIC_Ideal = ifelse(!is.null(res$aic_values), res$aic_values["Model2"], NA), AIC_Hybrid = ifelse(!is.null(res$aic_values), res$aic_values["Model3"], NA), R2_Average = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[1], NA), R2_Ideal = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[2], NA), R2_Hybrid = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[3], NA), Best_Model = res$best_model, N_Avg = res$sample_sizes$after_attention[1], N_Ideal = res$sample_sizes$after_attention[2], N_Reas = res$sample_sizes$after_attention[3], stringsAsFactors = FALSE))
  }
}

# Display summary table - THIS WILL RENDER CORRECTLY IN KNITTED HTML
kable(country_aic_summary_median_no3sd_smallval, caption = "AIC/R² by Country (Median, NO 3SD, Log Small Constant)", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  column_spec(8, background = case_when( is.na(country_aic_summary_median_no3sd_smallval$Best_Model) ~ "white", country_aic_summary_median_no3sd_smallval$Best_Model == "Hybrid" ~ "#e6f7ff", country_aic_summary_median_no3sd_smallval$Best_Model == "Average" ~ "#e6ffe6", country_aic_summary_median_no3sd_smallval$Best_Model == "Ideal" ~ "#ffe6e6", TRUE ~ "#f2f2f2" ))
```

#### 7b (Plus one to all values): Country Regressions (NO 3SD Removal)

```{r}
# Create storage
country_results_median_no3sd_plusone <- list()

# Function to analyze median data for a single country (NO 3SD, Plus One Log)
analyze_country_median_no3sd_plusone <- function(country, data_avg, data_ideal, data_reas, q_cols) {
  cat("\n========== Analyzing Median Data (NO 3SD, Log+1) for:", country, "==========\n")

  # Filter data by country AND apply attention check (using _Pass1 data)
  country_average_pass <- data_avg %>% filter(Country_name == country, q19 == 15)
  country_ideal_pass <- data_ideal %>% filter(Country_name == country, q19 == 15)
  country_reasonable_pass <- data_reas %>% filter(Country_name == country, q19 == 15)

  n_avg <- nrow(country_average_pass)
  n_ideal <- nrow(country_ideal_pass)
  n_reas <- nrow(country_reasonable_pass)

  cat("Participants after attention check:", n_avg, n_ideal, n_reas, "\n")

  if(n_avg < 1 || n_ideal < 1 || n_reas < 1) {
      cat("Insufficient participants for", country, "\n"); return(NULL)
  }

   convert_to_numeric <- function(df, cols) { df %>% mutate(across(all_of(cols), ~ suppressWarnings(as.numeric(as.character(.))))) }
   country_average_pass <- convert_to_numeric(country_average_pass, q_cols)
   country_ideal_pass <- convert_to_numeric(country_ideal_pass, q_cols)
   country_reasonable_pass <- convert_to_numeric(country_reasonable_pass, q_cols)

  # Calculate medians
  medians_avg <- if(n_avg > 0) sapply(country_average_pass[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_ideal <- if(n_ideal > 0) sapply(country_ideal_pass[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_reas <- if(n_reas > 0) sapply(country_reasonable_pass[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  names(medians_avg) <- q_cols; names(medians_ideal) <- q_cols; names(medians_reas) <- q_cols

  # Convert to log scale (Plus One)
  log_medians_avg <- log_plus_one(medians_avg)
  log_medians_ideal <- log_plus_one(medians_ideal)
  log_medians_reas <- log_plus_one(medians_reas)

  # Data frame for regression
  data_for_aic <- data.frame(Reasonable = log_medians_reas, Average = log_medians_avg, Ideal = log_medians_ideal)
  data_for_aic_clean <- data_for_aic %>% filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

  # Check for sufficient data points for regression
  if(nrow(data_for_aic_clean) < 5) {
    cat("Too few valid data points for regression analysis in", country, "\n")
    return(list(country=country, sample_sizes=list(after_attention=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_summary=NULL, best_model="Insufficient Data"))
  }

  # Run Regressions
  model1 <- lm(Reasonable ~ Average, data = data_for_aic_clean)
  aic1 <- AIC(model1); r2_1 <- summary(model1)$r.squared
  model2 <- lm(Reasonable ~ Ideal, data = data_for_aic_clean)
  aic2 <- AIC(model2); r2_2 <- summary(model2)$r.squared
  model3 <- lm(Reasonable ~ Average + Ideal, data = data_for_aic_clean)
  aic3 <- AIC(model3); r2_3 <- summary(model3)$r.squared

  # Regression summary
  reg_summary <- data.frame(Model=c("Avg", "Ideal", "Both"), AIC=c(aic1, aic2, aic3), R_squared=c(r2_1, r2_2, r2_3))
  best_model_idx <- which.min(c(aic1, aic2, aic3))
  best_model_name <- c("Average", "Ideal", "Hybrid")[best_model_idx]

  cat("Best model (NO 3SD, Log+1):", best_model_name, "\n") # Keep this text output if desired

  return(list(country=country, sample_sizes=list(after_attention=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_models=list(model1=model1, model2=model2, model3=model3), regression_summary=reg_summary, aic_values=c(Model1=aic1, Model2=aic2, Model3=aic3), best_model=best_model_name))
}

# Run analysis for each country
for(country in countries) {
  country_results_median_no3sd_plusone[[country]] <- analyze_country_median_no3sd_plusone(country, Data_All_Average_Pass1, Data_All_Ideal_Pass1, Data_All_Reasonable_Pass1, question_cols)
}

# Extract AIC summary
country_aic_summary_median_no3sd_plusone <- data.frame( Country = character(), AIC_Average = numeric(), AIC_Ideal = numeric(), AIC_Hybrid = numeric(), R2_Average = numeric(), R2_Ideal = numeric(), R2_Hybrid = numeric(), Best_Model = character(), N_Avg = integer(), N_Ideal = integer(), N_Reas = integer(), stringsAsFactors = FALSE )
for(country in countries) {
  res <- country_results_median_no3sd_plusone[[country]]
  if(!is.null(res)) {
      country_aic_summary_median_no3sd_plusone <- rbind(country_aic_summary_median_no3sd_plusone, data.frame( Country = country, AIC_Average = ifelse(!is.null(res$aic_values), res$aic_values["Model1"], NA), AIC_Ideal = ifelse(!is.null(res$aic_values), res$aic_values["Model2"], NA), AIC_Hybrid = ifelse(!is.null(res$aic_values), res$aic_values["Model3"], NA), R2_Average = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[1], NA), R2_Ideal = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[2], NA), R2_Hybrid = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[3], NA), Best_Model = res$best_model, N_Avg = res$sample_sizes$after_attention[1], N_Ideal = res$sample_sizes$after_attention[2], N_Reas = res$sample_sizes$after_attention[3], stringsAsFactors = FALSE))
  }
}

# Display summary table - THIS WILL RENDER CORRECTLY IN KNITTED HTML
kable(country_aic_summary_median_no3sd_plusone, caption = "AIC/R² by Country (Median, NO 3SD, Log Plus One)", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  column_spec(8, background = case_when( is.na(country_aic_summary_median_no3sd_plusone$Best_Model) ~ "white", country_aic_summary_median_no3sd_plusone$Best_Model == "Hybrid" ~ "#e6f7ff", country_aic_summary_median_no3sd_plusone$Best_Model == "Average" ~ "#e6ffe6", country_aic_summary_median_no3sd_plusone$Best_Model == "Ideal" ~ "#ffe6e6", TRUE ~ "#f2f2f2" ))
```
# Analysis 7 [WITH 3 SD Removed]

#### 7a (Small constant inf values): Country Regressions (WITH 3SD Removal)

```{r}
# Create storage
country_results_median_3sd_smallval <- list()

# Function to analyze median data for a single country (WITH 3SD, Small Constant Log)
analyze_country_median_3sd_smallval <- function(country, data_avg_filtered, data_ideal_filtered, data_reas_filtered, q_cols) {
  cat("\n========== Analyzing Median Data (WITH 3SD, Log Small Const) for:", country, "==========\n")

  # Filter data by country (using _Filtered data)
  country_average_final <- data_avg_filtered %>% filter(Country_name == country)
  country_ideal_final <- data_ideal_filtered %>% filter(Country_name == country)
  country_reasonable_final <- data_reas_filtered %>% filter(Country_name == country)

  n_avg <- nrow(country_average_final)
  n_ideal <- nrow(country_ideal_final)
  n_reas <- nrow(country_reasonable_final)

  cat("Participants after ALL filters:", n_avg, n_ideal, n_reas, "\n")

  if(n_avg < 1 || n_ideal < 1 || n_reas < 1) {
      cat("Insufficient participants for", country, "\n"); return(NULL)
  }

   # Columns should already be numeric from section 3, but double-check
   convert_to_numeric <- function(df, cols) { df %>% mutate(across(all_of(cols), ~ suppressWarnings(as.numeric(as.character(.))))) }
   country_average_final <- convert_to_numeric(country_average_final, q_cols)
   country_ideal_final <- convert_to_numeric(country_ideal_final, q_cols)
   country_reasonable_final <- convert_to_numeric(country_reasonable_final, q_cols)

  # Calculate medians
  medians_avg <- if(n_avg > 0) sapply(country_average_final[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_ideal <- if(n_ideal > 0) sapply(country_ideal_final[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_reas <- if(n_reas > 0) sapply(country_reasonable_final[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  names(medians_avg) <- q_cols; names(medians_ideal) <- q_cols; names(medians_reas) <- q_cols

  # Convert to log scale (Small Constant)
  log_medians_avg <- log_smallvalue(medians_avg)
  log_medians_ideal <- log_smallvalue(medians_ideal)
  log_medians_reas <- log_smallvalue(medians_reas)

  # Data frame for regression
  data_for_aic <- data.frame(Reasonable = log_medians_reas, Average = log_medians_avg, Ideal = log_medians_ideal)
  data_for_aic_clean <- data_for_aic %>% filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

  # Check for sufficient data points for regression
  if(nrow(data_for_aic_clean) < 5) {
    cat("Too few valid data points for regression analysis in", country, "\n")
    return(list(country=country, sample_sizes=list(after_all_filters=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_summary=NULL, best_model="Insufficient Data"))
  }

  # Run Regressions
  model1 <- lm(Reasonable ~ Average, data = data_for_aic_clean)
  aic1 <- AIC(model1); r2_1 <- summary(model1)$r.squared
  model2 <- lm(Reasonable ~ Ideal, data = data_for_aic_clean)
  aic2 <- AIC(model2); r2_2 <- summary(model2)$r.squared
  model3 <- lm(Reasonable ~ Average + Ideal, data = data_for_aic_clean)
  aic3 <- AIC(model3); r2_3 <- summary(model3)$r.squared

  # Regression summary
  reg_summary <- data.frame(Model=c("Avg", "Ideal", "Both"), AIC=c(aic1, aic2, aic3), R_squared=c(r2_1, r2_2, r2_3))
  best_model_idx <- which.min(c(aic1, aic2, aic3))
  best_model_name <- c("Average", "Ideal", "Hybrid")[best_model_idx]

  cat("Best model (WITH 3SD, Log Small Const):", best_model_name, "\n") # Keep this text output if desired

  return(list(country=country, sample_sizes=list(after_all_filters=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_models=list(model1=model1, model2=model2, model3=model3), regression_summary=reg_summary, aic_values=c(Model1=aic1, Model2=aic2, Model3=aic3), best_model=best_model_name))
}

# Run analysis for each country
for(country in countries) {
  country_results_median_3sd_smallval[[country]] <- analyze_country_median_3sd_smallval(country, Data_All_Average_Filtered, Data_All_Ideal_Filtered, Data_All_Reasonable_Filtered, question_cols)
}

# Extract AIC summary
country_aic_summary_median_3sd_smallval <- data.frame( Country = character(), AIC_Average = numeric(), AIC_Ideal = numeric(), AIC_Hybrid = numeric(), R2_Average = numeric(), R2_Ideal = numeric(), R2_Hybrid = numeric(), Best_Model = character(), N_Avg = integer(), N_Ideal = integer(), N_Reas = integer(), stringsAsFactors = FALSE )
for(country in countries) {
  res <- country_results_median_3sd_smallval[[country]]
  if(!is.null(res)) {
      country_aic_summary_median_3sd_smallval <- rbind(country_aic_summary_median_3sd_smallval, data.frame( Country = country, AIC_Average = ifelse(!is.null(res$aic_values), res$aic_values["Model1"], NA), AIC_Ideal = ifelse(!is.null(res$aic_values), res$aic_values["Model2"], NA), AIC_Hybrid = ifelse(!is.null(res$aic_values), res$aic_values["Model3"], NA), R2_Average = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[1], NA), R2_Ideal = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[2], NA), R2_Hybrid = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[3], NA), Best_Model = res$best_model, N_Avg = res$sample_sizes$after_all_filters[1], N_Ideal = res$sample_sizes$after_all_filters[2], N_Reas = res$sample_sizes$after_all_filters[3], stringsAsFactors = FALSE))
  }
}

# Display summary table - THIS WILL RENDER CORRECTLY IN KNITTED HTML
kable(country_aic_summary_median_3sd_smallval, caption = "AIC/R² by Country (Median, WITH 3SD, Log Small Constant)", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  column_spec(8, background = case_when( is.na(country_aic_summary_median_3sd_smallval$Best_Model) ~ "white", country_aic_summary_median_3sd_smallval$Best_Model == "Hybrid" ~ "#e6f7ff", country_aic_summary_median_3sd_smallval$Best_Model == "Average" ~ "#e6ffe6", country_aic_summary_median_3sd_smallval$Best_Model == "Ideal" ~ "#ffe6e6", TRUE ~ "#f2f2f2" ))
```
#### 7b (Plus one to all values): Country Regressions (WITH 3SD Removal)

```{r}
# Create storage
country_results_median_3sd_plusone <- list()

# Function to analyze median data for a single country (WITH 3SD, Plus One Log)
analyze_country_median_3sd_plusone <- function(country, data_avg_filtered, data_ideal_filtered, data_reas_filtered, q_cols) {
  cat("\n========== Analyzing Median Data (WITH 3SD, Log+1) for:", country, "==========\n")

  # Filter data by country (using _Filtered data)
  country_average_final <- data_avg_filtered %>% filter(Country_name == country)
  country_ideal_final <- data_ideal_filtered %>% filter(Country_name == country)
  country_reasonable_final <- data_reas_filtered %>% filter(Country_name == country)

  n_avg <- nrow(country_average_final)
  n_ideal <- nrow(country_ideal_final)
  n_reas <- nrow(country_reasonable_final)

  cat("Participants after ALL filters:", n_avg, n_ideal, n_reas, "\n")

  if(n_avg < 1 || n_ideal < 1 || n_reas < 1) {
      cat("Insufficient participants for", country, "\n"); return(NULL)
  }

   convert_to_numeric <- function(df, cols) { df %>% mutate(across(all_of(cols), ~ suppressWarnings(as.numeric(as.character(.))))) }
   country_average_final <- convert_to_numeric(country_average_final, q_cols)
   country_ideal_final <- convert_to_numeric(country_ideal_final, q_cols)
   country_reasonable_final <- convert_to_numeric(country_reasonable_final, q_cols)

  # Calculate medians
  medians_avg <- if(n_avg > 0) sapply(country_average_final[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_ideal <- if(n_ideal > 0) sapply(country_ideal_final[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  medians_reas <- if(n_reas > 0) sapply(country_reasonable_final[, q_cols], median, na.rm = TRUE) else rep(NA, length(q_cols))
  names(medians_avg) <- q_cols; names(medians_ideal) <- q_cols; names(medians_reas) <- q_cols

  # Convert to log scale (Plus One)
  log_medians_avg <- log_plus_one(medians_avg)
  log_medians_ideal <- log_plus_one(medians_ideal)
  log_medians_reas <- log_plus_one(medians_reas)

  # Data frame for regression
  data_for_aic <- data.frame(Reasonable = log_medians_reas, Average = log_medians_avg, Ideal = log_medians_ideal)
  data_for_aic_clean <- data_for_aic %>% filter(is.finite(Reasonable) & is.finite(Average) & is.finite(Ideal))

  # Check for sufficient data points for regression
  if(nrow(data_for_aic_clean) < 5) {
    cat("Too few valid data points for regression analysis in", country, "\n")
    return(list(country=country, sample_sizes=list(after_all_filters=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_summary=NULL, best_model="Insufficient Data"))
  }

  # Run Regressions
  model1 <- lm(Reasonable ~ Average, data = data_for_aic_clean)
  aic1 <- AIC(model1); r2_1 <- summary(model1)$r.squared
  model2 <- lm(Reasonable ~ Ideal, data = data_for_aic_clean)
  aic2 <- AIC(model2); r2_2 <- summary(model2)$r.squared
  model3 <- lm(Reasonable ~ Average + Ideal, data = data_for_aic_clean)
  aic3 <- AIC(model3); r2_3 <- summary(model3)$r.squared

  # Regression summary
  reg_summary <- data.frame(Model=c("Avg", "Ideal", "Both"), AIC=c(aic1, aic2, aic3), R_squared=c(r2_1, r2_2, r2_3))
  best_model_idx <- which.min(c(aic1, aic2, aic3))
  best_model_name <- c("Average", "Ideal", "Hybrid")[best_model_idx]

  cat("Best model (WITH 3SD, Log+1):", best_model_name, "\n") # Keep this text output if desired

  return(list(country=country, sample_sizes=list(after_all_filters=c(n_avg, n_ideal, n_reas)), medians=list(average=medians_avg, ideal=medians_ideal, reasonable=medians_reas), log_medians=list(average=log_medians_avg, ideal=log_medians_ideal, reasonable=log_medians_reas), regression_models=list(model1=model1, model2=model2, model3=model3), regression_summary=reg_summary, aic_values=c(Model1=aic1, Model2=aic2, Model3=aic3), best_model=best_model_name))
}

# Run analysis for each country
for(country in countries) {
  country_results_median_3sd_plusone[[country]] <- analyze_country_median_3sd_plusone(country, Data_All_Average_Filtered, Data_All_Ideal_Filtered, Data_All_Reasonable_Filtered, question_cols)
}

# Extract AIC summary
country_aic_summary_median_3sd_plusone <- data.frame( Country = character(), AIC_Average = numeric(), AIC_Ideal = numeric(), AIC_Hybrid = numeric(), R2_Average = numeric(), R2_Ideal = numeric(), R2_Hybrid = numeric(), Best_Model = character(), N_Avg = integer(), N_Ideal = integer(), N_Reas = integer(), stringsAsFactors = FALSE )
for(country in countries) {
  res <- country_results_median_3sd_plusone[[country]]
  if(!is.null(res)) {
      country_aic_summary_median_3sd_plusone <- rbind(country_aic_summary_median_3sd_plusone, data.frame( Country = country, AIC_Average = ifelse(!is.null(res$aic_values), res$aic_values["Model1"], NA), AIC_Ideal = ifelse(!is.null(res$aic_values), res$aic_values["Model2"], NA), AIC_Hybrid = ifelse(!is.null(res$aic_values), res$aic_values["Model3"], NA), R2_Average = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[1], NA), R2_Ideal = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[2], NA), R2_Hybrid = ifelse(!is.null(res$regression_summary), res$regression_summary$R_squared[3], NA), Best_Model = res$best_model, N_Avg = res$sample_sizes$after_all_filters[1], N_Ideal = res$sample_sizes$after_all_filters[2], N_Reas = res$sample_sizes$after_all_filters[3], stringsAsFactors = FALSE))
  }
}

# Display summary table - THIS WILL RENDER CORRECTLY IN KNITTED HTML
kable(country_aic_summary_median_3sd_plusone, caption = "AIC/R² by Country (Median, WITH 3SD, Log Plus One)", digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
  column_spec(8, background = case_when( is.na(country_aic_summary_median_3sd_plusone$Best_Model) ~ "white", country_aic_summary_median_3sd_plusone$Best_Model == "Hybrid" ~ "#e6f7ff", country_aic_summary_median_3sd_plusone$Best_Model == "Average" ~ "#e6ffe6", country_aic_summary_median_3sd_plusone$Best_Model == "Ideal" ~ "#ffe6e6", TRUE ~ "#f2f2f2" ))
```
# Analysis 8 [NO 3 SD Removed]

```{r}
# Create storage
country_intermediacy_results_median_no3sd <- list()

# Function to analyze median intermediacy for a single country (NO 3SD)
analyze_country_intermediacy_median_no3sd <- function(country, country_results_list) {
  cat("\n========== Analyzing Median Intermediacy (NO 3SD) for:", country, "==========\n")

  # Use the median data from Analysis 7 NO 3SD
  if(is.null(country_results_list[[country]]) || is.null(country_results_list[[country]]$medians)) {
    cat("No valid median data from Analysis 7 for", country, "\n"); return(NULL)
  }
  medians_avg <- country_results_list[[country]]$medians$average
  medians_ideal <- country_results_list[[country]]$medians$ideal
  medians_reas <- country_results_list[[country]]$medians$reasonable

  if(all(is.na(medians_avg)) || all(is.na(medians_ideal)) || all(is.na(medians_reas))){
      cat("Median vectors contain only NAs for", country, "\n"); return(NULL)
  }

  # --- Calculate vectors, counts, and p-values for all categories ---
  ideal_vec <- mapply(is_ideal_side_median, medians_avg, medians_ideal, medians_reas)
  ideal_count <- sum(ideal_vec, na.rm=TRUE); ideal_n <- sum(!is.na(ideal_vec))
  ideal_p <- if(ideal_n > 0) binom.test(ideal_count, ideal_n, p=0.5, alternative = "greater")$p.value else NA

  avg_vec <- mapply(is_average_side_median, medians_avg, medians_ideal, medians_reas)
  avg_count <- sum(avg_vec, na.rm=TRUE); avg_n <- sum(!is.na(avg_vec))
  avg_p <- if(avg_n > 0) binom.test(avg_count, avg_n, p=0.5, alternative = "greater")$p.value else NA

  both_vec_liberal <- mapply(is_both_sides_median_liberal, medians_avg, medians_ideal, medians_reas)
  both_count_liberal <- sum(both_vec_liberal, na.rm=TRUE); both_n_liberal <- sum(!is.na(both_vec_liberal))
  liberal_p <- if(both_n_liberal > 0) binom.test(both_count_liberal, both_n_liberal, p=1/3, alternative = "two.sided")$p.value else NA

  both_vec_conservative <- mapply(is_both_sides_median_conservative, medians_avg, medians_ideal, medians_reas)
  both_count_conservative <- sum(both_vec_conservative, na.rm=TRUE); both_n_conservative <- sum(!is.na(both_vec_conservative))
  conservative_p <- if(both_n_conservative > 0) binom.test(both_count_conservative, both_n_conservative, p=1/3, alternative = "two.sided")$p.value else NA

  # Return a comprehensive list of results
  return(list(
    country=country,
    ideal_side=list(prop=ideal_count/ideal_n, p_val=ideal_p),
    average_side=list(prop=avg_count/avg_n, p_val=avg_p),
    between_liberal=list(prop=both_count_liberal/both_n_liberal, p_val=liberal_p),
    between_conservative=list(prop=both_count_conservative/both_n_conservative, p_val=conservative_p)
  ))
}

# Run analysis for each country
analysis_7_results_no3sd_source <- country_results_median_no3sd_plusone
country_intermediacy_results_median_no3sd <- lapply(countries, analyze_country_intermediacy_median_no3sd, analysis_7_results_no3sd_source)

# Create the summary data frame from the results
intermediacy_by_country_median_no3sd <- do.call(rbind, lapply(country_intermediacy_results_median_no3sd, function(res) {
    if (is.null(res)) return(NULL)
    data.frame(
        Country = res$country,
        Ideal_Prop = res$ideal_side$prop, Ideal_P = res$ideal_side$p_val,
        Avg_Prop = res$average_side$prop, Avg_P = res$average_side$p_val,
        Between_Prop_Liberal = res$between_liberal$prop, Between_P_Liberal = res$between_liberal$p_val,
        Between_Prop_Conservative = res$between_conservative$prop, Between_P_Conservative = res$between_conservative$p_val
    )
}))

# Format and display the final table
display_summary_no3sd <- intermediacy_by_country_median_no3sd %>%
  mutate(
    Ideal_Side_Pct = scales::percent(Ideal_Prop, accuracy = 0.1),
    Ideal_Sig = ifelse(!is.na(Ideal_P) & Ideal_P < 0.05, "*", ""),
    Average_Side_Pct = scales::percent(Avg_Prop, accuracy = 0.1),
    Average_Sig = ifelse(!is.na(Avg_P) & Avg_P < 0.05, "*", ""),
    Between_Liberal_Pct = scales::percent(Between_Prop_Liberal, accuracy = 0.1),
    Between_Liberal_Sig = ifelse(!is.na(Between_P_Liberal) & Between_P_Liberal < 0.05, "*", ""),
    Between_Conservative_Pct = scales::percent(Between_Prop_Conservative, accuracy = 0.1),
    Between_Conservative_Sig = ifelse(!is.na(Between_P_Conservative) & Between_P_Conservative < 0.05, "*", "")
  ) %>%
  arrange(desc(Between_Prop_Liberal)) %>%
  select(
    Country,
    `Ideal Side (%)` = Ideal_Side_Pct, ` ` = Ideal_Sig,
    `Average Side (%)` = Average_Side_Pct, `  ` = Average_Sig,
    `Between (Liberal %)` = Between_Liberal_Pct, `   ` = Between_Liberal_Sig,
    `Between (Conservative %)` = Between_Conservative_Pct, `    ` = Between_Conservative_Sig
  )

kable(display_summary_no3sd, caption = "Intermediacy Analysis by Country (NO 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
  add_header_above(c(" " = 1, "Ideal Side*" = 2, "Average Side*" = 2, "Liberal*" = 2, "Conservative*" = 2)) %>%
  column_spec(1, bold = T)
```

# Analysis 8 [WITH 3 SD Removed]

```{r}
# Create storage
country_intermediacy_results_median_3sd <- list()

# Function to analyze median intermediacy for a single country (WITH 3SD)
analyze_country_intermediacy_median_3sd <- function(country, country_results_list) {
  cat("\n========== Analyzing Median Intermediacy (WITH 3SD) for:", country, "==========\n")

  if(is.null(country_results_list[[country]]) || is.null(country_results_list[[country]]$medians)) {
    cat("No valid median data from Analysis 7 for", country, "\n"); return(NULL)
  }
  
  medians_avg <- country_results_list[[country]]$medians$average
  medians_ideal <- country_results_list[[country]]$medians$ideal
  medians_reas <- country_results_list[[country]]$medians$reasonable

  if(all(is.na(medians_avg)) || all(is.na(medians_ideal)) || all(is.na(medians_reas))){
      cat("Median vectors contain only NAs for", country, "\n"); return(NULL)
  }

  # --- Calculate all vectors ---
  ideal_vec <- mapply(is_ideal_side_median, medians_avg, medians_ideal, medians_reas)
  avg_vec <- mapply(is_average_side_median, medians_avg, medians_ideal, medians_reas)
  both_vec_liberal <- mapply(is_both_sides_median_liberal, medians_avg, medians_ideal, medians_reas)
  both_vec_conservative <- mapply(is_both_sides_median_conservative, medians_avg, medians_ideal, medians_reas)
  
  # --- P-values ---
  ideal_p <- if(sum(!is.na(ideal_vec)) > 0) binom.test(sum(ideal_vec, na.rm=T), sum(!is.na(ideal_vec)), p=0.5, alt="greater")$p.value else NA
  avg_p <- if(sum(!is.na(avg_vec)) > 0) binom.test(sum(avg_vec, na.rm=T), sum(!is.na(avg_vec)), p=0.5, alt="greater")$p.value else NA
  liberal_p <- if(sum(!is.na(both_vec_liberal)) > 0) binom.test(sum(both_vec_liberal, na.rm=T), sum(!is.na(both_vec_liberal)), p=1/3, alt="two.sided")$p.value else NA
  conservative_p <- if(sum(!is.na(both_vec_conservative)) > 0) binom.test(sum(both_vec_conservative, na.rm=T), sum(!is.na(both_vec_conservative)), p=1/3, alt="two.sided")$p.value else NA
  
  # --- Return all results in a single data frame row ---
  data.frame(
    Country = country,
    Ideal_Prop = sum(ideal_vec, na.rm=T) / sum(!is.na(ideal_vec)),
    Ideal_P = ideal_p,
    Avg_Prop = sum(avg_vec, na.rm=T) / sum(!is.na(avg_vec)),
    Avg_P = avg_p,
    Between_Prop_Liberal = sum(both_vec_liberal, na.rm=T) / sum(!is.na(both_vec_liberal)),
    Between_P_Liberal = liberal_p,
    Between_Prop_Conservative = sum(both_vec_conservative, na.rm=T) / sum(!is.na(both_vec_conservative)),
    Between_P_Conservative = conservative_p
  )
}

# --- Run analysis and build the summary table ---
analysis_7_results_3sd_source <- country_results_median_3sd_plusone
all_country_results_3sd <- do.call(rbind, lapply(countries, analyze_country_intermediacy_median_3sd, analysis_7_results_3sd_source))

# --- Create and display the combined summary table ---
display_summary_3sd <- all_country_results_3sd %>%
  mutate(
    Ideal_Side_Pct = scales::percent(Ideal_Prop, accuracy = 0.1),
    Ideal_Sig = ifelse(!is.na(Ideal_P) & Ideal_P < 0.05, "*", ""),
    Average_Side_Pct = scales::percent(Avg_Prop, accuracy = 0.1),
    Average_Sig = ifelse(!is.na(Avg_P) & Avg_P < 0.05, "*", ""),
    Between_Liberal_Pct = scales::percent(Between_Prop_Liberal, accuracy = 0.1),
    Between_Liberal_Sig = ifelse(!is.na(Between_P_Liberal) & Between_P_Liberal < 0.05, "*", ""),
    Between_Conservative_Pct = scales::percent(Between_Prop_Conservative, accuracy = 0.1),
    Between_Conservative_Sig = ifelse(!is.na(Between_P_Conservative) & Between_P_Conservative < 0.05, "*", "")
  ) %>%
  arrange(desc(Between_Prop_Liberal)) %>%
  select(
    Country,
    `Ideal Side (%)` = Ideal_Side_Pct, ` ` = Ideal_Sig,
    `Average Side (%)` = Average_Side_Pct, `  ` = Average_Sig,
    `Between (Liberal %)` = Between_Liberal_Pct, `   ` = Between_Liberal_Sig,
    `Between (Conservative %)` = Between_Conservative_Pct, `    ` = Between_Conservative_Sig
  )

kable(display_summary_3sd, caption = "Intermediacy Analysis by Country (WITH 3SD Removal)") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), full_width = F) %>%
  add_header_above(c(" " = 1, "Ideal Side*" = 2, "Average Side*" = 2, "Liberal*" = 2, "Conservative*" = 2)) %>%
  column_spec(1, bold = T)
```


# Plots for Publication

### Figure 1: Visualization of Reasonable Medians by Country and Item [NO 3 SD Removed] NEEDS REVISION

```{r}
# Create a mapping for question numbers to descriptive labels
question_labels <- c(
  "q1" = "Hrs TV / day", "q2" = "Sugary drinks / wk", "q3" = "Exercise hrs / wk",
  "q4" = "Calories / day", "q5" = "Vegetable servings / mo", "q6" = "Lies told / wk",
  "q7" = "Mins doctor late", "q8" = "Books read / yr", "q9" = "Romantic partners / life",
  "q10" = "Int'l conflicts / decade", "q11" = "Dollars cheated on taxes", "q12" = "% Cheating students",
  "q13" = "Phone checks / day", "q14" = "Mins phone wait time", "q15" = "Calls to parent / mo",
  "q16" = "House cleans / mo", "q17" = "Computer crashes / mo", "q18" = "% School dropouts",
  "q20" = "% Kids bullied", "q21" = "College bro drinks / wknd", "q22" = "Days to accept contract",
  "q23" = "Wks to return product", "q24" = "Hrs to reflect on offer", "q25" = "Extra costs ($10k build)",
  "q26" = "Wks construction delay", "q27" = "Loud events near homes / yr", "q28" = "% Car profits on safety",
  "q29" = "% Medical details desired", "q30" = "Wks wait for criminal trial", "q31" = "Hourly atty fee (charity)",
  "q32" = "Hrs landlord entry notice", "q33" = "Loan interest rate (%)", "q34" = "Polluter recidivism (%)"
)

# Prepare the data for visualization
prepare_figure1_data <- function() {
  # Extract country information
  countries <- unique(Data_All$Country_name)
  
  # Initialize empty dataframe
  figure1_data <- data.frame()
  
  # Add Poland expert category if it exists
  if("Poland_Expert" %in% countries) {
    countries <- countries[countries != "Poland_Expert"]
    countries <- c(countries, "Poland_Expert")
  }
  
  # Process each country
  for(country in countries) {
    country_name <- country
    if(country == "Poland_Expert") {
      country_filter <- "Poland"
      country_name <- "Poland_Expert"
    } else {
      country_filter <- country
    }
    
    # Filter by country and condition
    if(country == "Poland_Expert") {
      # Special handling for Poland expert data if needed
      country_avg <- Data_All_Average_Pass1 %>% 
        filter(Country_name == country_filter, Expert == TRUE)
      country_ideal <- Data_All_Ideal_Pass1 %>% 
        filter(Country_name == country_filter, Expert == TRUE)
      country_reasonable <- Data_All_Reasonable_Pass1 %>% 
        filter(Country_name == country_filter, Expert == TRUE)
    } else {
      country_avg <- Data_All_Average_Pass1 %>% 
        filter(Country_name == country_filter)
      country_ideal <- Data_All_Ideal_Pass1 %>% 
        filter(Country_name == country_filter)
      country_reasonable <- Data_All_Reasonable_Pass1 %>% 
        filter(Country_name == country_filter)
    }
    
    # Calculate medians for each question by condition
    for(q in question_cols) {
      if(q %in% colnames(country_avg) && q %in% colnames(country_ideal) && q %in% colnames(country_reasonable)) {
        # Calculate medians
        median_avg <- median(as.numeric(country_avg[[q]]), na.rm = TRUE)
        median_ideal <- median(as.numeric(country_ideal[[q]]), na.rm = TRUE)
        median_reasonable <- median(as.numeric(country_reasonable[[q]]), na.rm = TRUE)
        
        # Add to dataframe
        figure1_data <- rbind(figure1_data, data.frame(
          Country = country_name,
          Item = q,
          Median_average = median_avg,
          Median_ideal = median_ideal,
          Median_reasonable = median_reasonable
        ))
      }
    }
  }
  
  return(figure1_data)
}

# Generate the data
figure1_data <- prepare_figure1_data()

# Process the data to match the paper's visualization
processed_data <- figure1_data %>%
  mutate(
    Item_label = question_labels[Item],
    Color = ifelse(Median_reasonable >= Median_average & Median_reasonable <= Median_ideal |
                   Median_reasonable <= Median_average & Median_reasonable >= Median_ideal, 
                  "navy", "firebrick"),
    Shape = case_when(
      Median_ideal < Median_average ~ 'Less',      # Downward triangle
      Median_ideal > Median_average ~ 'More',      # Upward triangle  
      Median_ideal == Median_average ~ 'Equal'     # Circle
    ),
    Ratio = log2(Median_ideal/Median_average)
  )

# Calculate the ratio for ordering items
item_ratios <- processed_data %>%
  group_by(Item) %>%
  summarize(Avg_ratio = mean(Ratio, na.rm = TRUE))

# Join with the processed data
processed_data <- processed_data %>%
  left_join(item_ratios, by = "Item")

# Define country abbreviation labels
CountryLabels = c(
  'Brazil' = 'BR', 
  'Colombia' = 'CO',
  'Germany' = 'DE',
  'India' = 'IN',
  'Italy' = 'IT',
  'Lithuania' = 'LT',
  'Netherlands' = 'NL',
  'Poland' = 'PL',
  'Poland_Expert' = 'PL*',
  'Spain' = 'ES',
  'USA' = 'US'
)

# Update country names to use abbreviations for plotting
processed_data$Country_label <- CountryLabels[processed_data$Country]

# Create the figure
figure1_nofilter <- ggplot(processed_data, 
                  aes(x = Country, y = reorder(Item_label, Avg_ratio), 
                      fill = Color, color = Color)) + 
  geom_point(aes(shape = Shape), size = 5, alpha = 0.9, stroke = 1) + 
  geom_text(aes(label = round(Median_reasonable)), 
            size = 2.5, color = "white") + 
  scale_fill_identity() +
  scale_color_identity() +
  scale_shape_manual(values = c('Equal' = 21, 'Less' = 25, 'More' = 24)) +
  scale_x_discrete(labels = CountryLabels, position = "top") +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    legend.position = "none",
    text = element_text(color = "black"),
    axis.text.x = element_text(face = "bold", color = "black", size = 10),
    axis.text.y = element_text(size = 9),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

# Display the figure
print(figure1_nofilter)

# Save the figure
ggsave("Figure1_Reasonableness_NoFilter.jpg", figure1_nofilter, dpi = 300, width = 16, height = 25, units = "cm")
```

### Figure 1: Visualization of Reasonable Medians by Country and Item [WITH 3 SD Removed] NEEDS REVISION

```{r}
# Create a mapping for question numbers to descriptive labels
question_labels <- c(
  "q1" = "Hrs TV / day", "q2" = "Sugary drinks / wk", "q3" = "Exercise hrs / wk",
  "q4" = "Calories / day", "q5" = "Vegetable servings / mo", "q6" = "Lies told / wk",
  "q7" = "Mins doctor late", "q8" = "Books read / yr", "q9" = "Romantic partners / life",
  "q10" = "Int'l conflicts / decade", "q11" = "Dollars cheated on taxes", "q12" = "% Cheating students",
  "q13" = "Phone checks / day", "q14" = "Mins phone wait time", "q15" = "Calls to parent / mo",
  "q16" = "House cleans / mo", "q17" = "Computer crashes / mo", "q18" = "% School dropouts",
  "q20" = "% Kids bullied", "q21" = "College bro drinks / wknd", "q22" = "Days to accept contract",
  "q23" = "Wks to return product", "q24" = "Hrs to reflect on offer", "q25" = "Extra costs ($10k build)",
  "q26" = "Wks construction delay", "q27" = "Loud events near homes / yr", "q28" = "% Car profits on safety",
  "q29" = "% Medical details desired", "q30" = "Wks wait for criminal trial", "q31" = "Hourly atty fee (charity)",
  "q32" = "Hrs landlord entry notice", "q33" = "Loan interest rate (%)", "q34" = "Polluter recidivism (%)"
)

# Prepare the data for visualization
prepare_figure1_data <- function() {
  # Extract country information
  countries <- unique(Data_All$Country_name)
  
  # Initialize empty dataframe
  figure1_data <- data.frame()
  
  # Add Poland expert category if it exists
  if("Poland_Expert" %in% countries) {
    countries <- countries[countries != "Poland_Expert"]
    countries <- c(countries, "Poland_Expert")
  }
  
  # Process each country
  for(country in countries) {
    country_name <- country
    if(country == "Poland_Expert") {
      country_filter <- "Poland"
      country_name <- "Poland_Expert"
    } else {
      country_filter <- country
    }
    
    # Filter by country and condition
    if(country == "Poland_Expert") {
      # Special handling for Poland expert data if needed
      country_avg <- Data_All_Average_Filtered %>% 
        filter(Country_name == country_filter, Expert == TRUE)
      country_ideal <- Data_All_Ideal_Filtered %>% 
        filter(Country_name == country_filter, Expert == TRUE)
      country_reasonable <- Data_All_Reasonable_Filtered %>% 
        filter(Country_name == country_filter, Expert == TRUE)
    } else {
      country_avg <- Data_All_Average_Filtered %>% 
        filter(Country_name == country_filter)
      country_ideal <- Data_All_Ideal_Filtered %>% 
        filter(Country_name == country_filter)
      country_reasonable <- Data_All_Reasonable_Filtered %>% 
        filter(Country_name == country_filter)
    }
    
    # Calculate medians for each question by condition
    for(q in question_cols) {
      if(q %in% colnames(country_avg) && q %in% colnames(country_ideal) && q %in% colnames(country_reasonable)) {
        # Calculate medians
        median_avg <- median(as.numeric(country_avg[[q]]), na.rm = TRUE)
        median_ideal <- median(as.numeric(country_ideal[[q]]), na.rm = TRUE)
        median_reasonable <- median(as.numeric(country_reasonable[[q]]), na.rm = TRUE)
        
        # Add to dataframe
        figure1_data <- rbind(figure1_data, data.frame(
          Country = country_name,
          Item = q,
          Median_average = median_avg,
          Median_ideal = median_ideal,
          Median_reasonable = median_reasonable
        ))
      }
    }
  }
  
  return(figure1_data)
}

# Generate the data
figure1_data <- prepare_figure1_data()

# Process the data to match the paper's visualization
processed_data <- figure1_data %>%
  mutate(
    Item_label = question_labels[Item],
    Color = ifelse(Median_reasonable >= Median_average & Median_reasonable <= Median_ideal |
                   Median_reasonable <= Median_average & Median_reasonable >= Median_ideal, 
                  "navy", "firebrick"),
    Shape = case_when(
      Median_ideal < Median_average ~ 'Less',      # Downward triangle
      Median_ideal > Median_average ~ 'More',      # Upward triangle  
      Median_ideal == Median_average ~ 'Equal'     # Circle
    ),
    Ratio = log2(Median_ideal/Median_average)
  )

# Calculate the ratio for ordering items
item_ratios <- processed_data %>%
  group_by(Item) %>%
  summarize(Avg_ratio = mean(Ratio, na.rm = TRUE))

# Join with the processed data
processed_data <- processed_data %>%
  left_join(item_ratios, by = "Item")

# Define country abbreviation labels
CountryLabels = c(
  'Brazil' = 'BR', 
  'Colombia' = 'CO',
  'Germany' = 'DE',
  'India' = 'IN',
  'Italy' = 'IT',
  'Lithuania' = 'LT',
  'Netherlands' = 'NL',
  'Poland' = 'PL',
  'Poland_Expert' = 'PL*',
  'Spain' = 'ES',
  'USA' = 'US'
)

# Update country names to use abbreviations for plotting
processed_data$Country_label <- CountryLabels[processed_data$Country]

# Create the figure
figure1_filtered <- ggplot(processed_data, 
                  aes(x = Country, y = reorder(Item_label, Avg_ratio), 
                      fill = Color, color = Color)) + 
  geom_point(aes(shape = Shape), size = 5, alpha = 0.9, stroke = 1) + 
  geom_text(aes(label = round(Median_reasonable)), 
            size = 2.5, color = "white") + 
  scale_fill_identity() +
  scale_color_identity() +
  scale_shape_manual(values = c('Equal' = 21, 'Less' = 25, 'More' = 24)) +
  scale_x_discrete(labels = CountryLabels, position = "top") +
  theme_minimal() +
  theme(
    axis.title = element_blank(),
    legend.position = "none",
    text = element_text(color = "black"),
    axis.text.x = element_text(face = "bold", color = "black", size = 10),
    axis.text.y = element_text(size = 9),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

# Display the figure
print(figure1_filtered)

# Save the figure
ggsave("Figure1_Reasonableness_Filtered.jpg", figure1_filtered, dpi = 300, width = 16, height = 25, units = "cm")
```
### Table 3 for Paper

```{r}
# 1. Define question labels (if not already defined in your script)
question_labels <- c(
  "q1" = "Hrs TV / day", "q2" = "Sugary drinks / wk", "q3" = "Exercise hrs / wk",
  "q4" = "Calories / day", "q5" = "Vegetable servings / mo", "q6" = "Lies told / wk",
  "q7" = "Mins doctor late", "q8" = "Books read / yr", "q9" = "Romantic partners / life",
  "q10" = "Int'l conflicts / decade", "q11" = "Dollars cheated on taxes", "q12" = "% Cheating students",
  "q13" = "Phone checks / day", "q14" = "Mins phone wait time", "q15" = "Calls to parent / mo",
  "q16" = "House cleans / mo", "q17" = "Computer crashes / mo", "q18" = "% School dropouts",
  "q20" = "% Kids bullied", "q21" = "College bro drinks / wknd", "q22" = "Days to accept contract",
  "q23" = "Wks to return product", "q24" = "Hrs to reflect on offer", "q25" = "Extra costs ($10k build)",
  "q26" = "Wks construction delay", "q27" = "Loud events near homes / yr", "q28" = "% Car profits on safety",
  "q29" = "% Medical details desired", "q30" = "Wks wait for criminal trial", "q31" = "Hourly atty fee (charity)",
  "q32" = "Hrs landlord entry notice", "q33" = "Loan interest rate (%)", "q34" = "Polluter recidivism (%)"
)

# 2. Run the function to prepare the data (ensure this function is defined in your script)
# This calculates the by-country, by-item medians for all conditions.
all_medians_data <- prepare_figure1_data()

# 3. Add labels, select, and format the full dataset
all_medians_table <- all_medians_data %>%
  # Create the Item_label column from the question codes
  mutate(Item_label = question_labels[Item]) %>%
  # Select and rename columns for clarity
  select(Country,
         `Item Label` = Item_label,
         Average = Median_average,
         Reasonable = Median_reasonable,
         Ideal = Median_ideal) %>%
  # Arrange the results alphabetically by Country, then by Item Label
  arrange(Country, `Item Label`)

# 4. Display the complete results in a clean table
# In RStudio, this will produce a nice, scrollable table.
kable(all_medians_table,
      caption = "Complete By-Country, By-Item Median Values",
      format = "pipe",
      align = "lrrrr")
```

